### 2016-06-18 derivation_supplementary/supplementary.tex
up

% Created 2016-06-19 Sun 00:51
\documentclass[colorlinks]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\hypersetup{allcolors = blue} % to have all the hyperlinks in 1 color
\renewcommand{\refname}{\vspace{-.8cm}}
\usepackage{jneurosci}
\bibliographystyle{jneurosci}
\author{Y. Zerlaut \& A. Destexhe}
\date{\today}
\title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\tableofcontents

\newpage

\section{Reduction to the equivalent cylinder}
\label{sec-1}
\label{sec:reduction-to-eq-cyl}

The key of the derivation relies on having the possibility to reduce
the complex morphology to an equivalent cylinder \cite{Rall1962}. We
adapted this procedure to capture the change in integrative properties
of the membrane that results from the mean synaptic bombardment during
active cortical states, reviewed in \citetext{Destexhe2003}.

For a set of synaptic stimulation \(\{\nu^e_p, \nu_i^p, \nu_e^d,
\nu_i^d, s\}\), let's introduce the following stationary densities of
conductances:

\begin{equation}
\left\{
\begin{split}
& g_{e0}^p = \pi \, d \, \mathcal{D}_e \, \nu_e^p \, \tau_e^p \, Q_e^p \quad ;  \quad
g_{i0}^p = \pi \, d \, \mathcal{D}_i \, \nu_i^p \, \tau_i^p \, Q_i^p \\
& g_{e0}^d = \pi \, d \, \mathcal{D}_e  \, \nu_e^d \, \tau_e^d \, Q_e^d \quad ; \quad 
g_{i0}^d = \pi \, d \, \mathcal{D}_i \, \nu_i^d \, \tau_i^d \, Q_i^d
\end{split}
\right.
\end{equation}

where $\mathcal{D}_e$ and $\mathcal{D}_i$ are the excitatory and
inhibitory synaptic densities.

We introduce two activity-dependent electrotonic constants relative to
the proximal and distal part respectively:

\begin{equation}
\lambda^p= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^p + r_m g_{i0}^p)}}
\quad 
\lambda^d= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^d + r_m g_{i0}^d)}}$
\end{equation}

For a dendritic tree of total length $l$, whose proximal part ends at
$l_p$ and with $B$ evenly spaced generations of branches, we define
the space-dependent electrotonic constant:

\begin{equation}
 \lambda(x) = \big( \lambda^p + \mathcal{H}(x-l_p)(\lambda^d-\lambda^p) \big)
 2^{- \frac{1}{3} \, \lfloor \frac{B \, x}{l} \rfloor}
\end{equation}

where \( \lfloor . \rfloor \) is the floor function. Note that
$\lambda(x)$ is constant on a given generation, but it decreases from
generation to generation because of the decreasing diameter along the
dendritic tree. It also depends on the synaptic activity and
therefore has a discontinuity at $x=l_p$.

Following \citetext{Rall1962}, we now define a dimensionless length $X$:

\begin{equation}
\label{eq:x-rescale}
 X(x) = \int_0^x \frac{dx}{\lambda(x)}
\end{equation}

We define \(L= X(l) \) and \(L_p= X(l_p) \), the total length and
proximal part length respectively (capital letters design rescaled
quantities).

\section{Mean membrane potential}
\label{sec-2}
\label{sec:mean-derivation}

We derive the mean membrane potential \(\mu_V(x)\) corresponding to
the stationary response to constant densities of conductances given by
the means of the synaptic stimulation. We obtain the stationary
equations by removing temporal derivatives in Equation, the set of
equation governing this mean membrane potential in all branches is
therefore:

\begin{equation}
\label{eq:model-equation-muV}
\left\{
\begin{split}
& \frac{1}{r_i} \frac{\partial^2 \mu_v}{\partial x^2} = \frac{\mu_v(x)-E_L}{r_m} \\
& \qquad - g_{e0}^p \, (\mu_v(x) - E_e) - g_{0i}^p \, (\mu_v(x) - E_i) \quad \forall x \in [0,l_p] \\
& \frac{1}{r_i} \frac{\partial^2 \mu_v}{\partial x^2} =  \frac{\mu_v(x)-E_L}{r_m} \\
& \qquad - g_{e0}^d \, (\mu_v(x) - E_e) - g_{0i}^d \, (\mu_v(x) - E_i)  \quad \forall x \in [l_p,l]  \\
& \frac{\partial \mu_v}{\partial x}_{|x=0} = r_i \, \big(
 \frac{\mu_v(0)-E_L}{R_m} + G_{i0}^S \, ( \mu_v(0)-E_i) \big)\\
& \mu_v(l_p^-,t) = \mu_v(l_p^+,t) \\
& \frac{\partial \mu_v}{\partial x}_{l_p^-} 
= \frac{\partial \mu_v}{\partial x}_{l_p^+} \\
& \frac{\partial \mu_v}{\partial x}_{x=l} = 0
\end{split}
\right.
\end{equation}

Because the reduction to the equivalent cylinder conserves the
membrane area and the previous equation only depends on density of
currents, the equation governing $\mu_v(x)$ in all branches can be
transformed into an equation on an equivalent cylinder of length $L$.
We rescale $x$ by $\lambda(x)$ (see Equation \ref{eq:x-rescale}) and we
obtain the equation verified by \(\mu_V(X)\):

\begin{equation}
\label{eq:model-equation-muV-rescaled}
\left\{
\begin{split}
& \frac{\partial^2 \mu_v}{\partial X^2} = \mu_v(X)-v_0^p \quad \forall X \in [0,L_p] \\
&\frac{\partial^2 \mu_v}{\partial X^2} = \mu_v(X)-v_0^d \quad \forall X \in [L_p,L]  \\
&\frac{\partial \mu_v}{\partial X}|_{X=0} = \gamma^p \, 
\Big( \mu_v(0) - V_0  \Big) \\
&\mu_v(L_p^-) = \mu_v(L_p^+) \\
&\frac{\partial \mu_v}{\partial X}_{L_p^-} = \frac{\lambda^p}{\lambda^d}
\frac{\partial \mu_v}{\partial X}_{L_p^+} \\
&\frac{\partial \mu_v}{\partial X}_{X=L} = 0 
\end{split}
\right.
\end{equation}

where:

\begin{equation}
\begin{split}
& v_0^p = \frac{E_L + r_m g_{e0}^p E_e + r_m g_{i0}^p E_i}{ 1 + r_m g_{e0}^p + r_m g_{i0}^p }\\
& v_0^d = \frac{E_L + r_m g_{e0}^d E_e + r_m g_{i0}^d E_i}{ 1 + r_m g_{e0}^d + r_m g_{i0}^d }\\
& \gamma^p = \frac{r_i \lambda^p \, (1+ G_i^0 R_m)}{R_m}\\
& V_0 = \frac{E_L + G_i^0 R_m E_i}{ 1 +  + G_i^0 R_m }
\end{split}
\end{equation}

We write the solution on the form:

\begin{equation}
\left\{
\begin{split}
& \mu_v(X) = v_0^p + A \, \cosh(X) + C \, \sinh(X) \quad \forall \, X \in [0,L_p] \\
& \mu_v(X) = v_0^d + B \, \cosh(X-L) + D \, \sinh(X-L) \quad \forall \, X \in [L_pL]
\end{split}
\right.
\end{equation}

\begin{itemize}
\item Sealed-end boundary condition at cable end implies $D=0$

\item Somatic boudary condition imply: $C = \gamma^p \, (v_0^p - V_0 + A)$

\item Then v continuity imply :
\( v_0^p + A \, \cosh(L_p) +  \gamma^p \, (v_0^p - V_0 + A) \, \sinh(L_p) = v_0^d + B \, \cosh(L_p-L) \)

\item Then current conservation imply: 
\( A \, \sinh(L_p) +  \gamma^p \, (v_0^p - V_0 + A) \, \cosh(L_p) = \frac{\lambda^p}{\lambda^d} \, B \, \sinh(L_p-L) \)
\end{itemize}

We rewrite those condition on a matrix form:

\begin{equation}
\Big(
\begin{matrix}
    \cosh(L_p)+\gamma^p \sinh(L_p) & -\cosh(L_p-L) \\
    \sinh(L_p)+\gamma^p \cosh(L_p) & -  \frac{\lambda^p}{\lambda^d} \, \sinh(L_p-L) 
\end{matrix}
\Big)
\cdot
\Big(
\begin{matrix}
    A \\
    B 
\end{matrix}
\Big) = 
\Big(
\begin{matrix}
v_0^d - v_0^p - \gamma^p \, (v_0^p-V_0) \, \sinh(L_p) \\
- \gamma^p \, (v_0^p-V_0) \, \cosh(L_p)
\end{matrix}
\Big)
\end{equation}

And we solved this equation with the \texttt{solve\_linear\_system\_LU} method of \texttt{sympy}

The coefficients $A$ and $B$ are given by:
\begin{equation}
A=\frac{\alpha}{\beta} \qquad \qquad B=\frac{\gamma}{\delta}
\end{equation}

where:

\begin{equation}
\begin{split}
& \alpha = V_{0} \gamma^{P} \lambda^{D} \cosh{\left (L_{p} \right )}
\cosh{\left (L - L_{p} \right )} + V_{0} \gamma^{P} \lambda^{P}
\sinh{\left (L_{p} \right )} \sinh{\left (L - L_{p} \right )} \\
& \quad - \gamma^{P} \lambda^{D} v^{d}_{0} \cosh{\left (L_{p} \right )}
\cosh{\left (L - L_{p} \right )} - \gamma^{P} \lambda^{P} v^{d}_{0}
\sinh{\left (L_{p} \right )} \sinh{\left (L - L_{p} \right )} \\
& \quad - \lambda^{P} v^{d}_{0} \sinh{\left (L - L_{p} \right )}
 + \lambda^{P} v^{p}_{0} \sinh{\left (L - L_{p} \right )} \\
& \beta = \gamma^{P} \lambda^{D} \cosh{\left (L_{p} \right )}
\cosh{\left (L - L_{p} \right )} + \gamma^{P} \lambda^{P} \sinh{\left
(L_{p} \right )} \sinh{\left (L - L_{p} \right )} + \\
& \quad \lambda^{D} \sinh{\left (L_{p} \right )} \cosh{\left (L - L_{p} \right )}
 + \lambda^{P} \sinh{\left (L - L_{p} \right )} \cosh{\left (L_{p} \right
)} \\
& \gamma = \lambda^{D} \big( V_{0} \gamma^{P} + \gamma^{P} v^{d}_{0}
\cosh{\left (L_{p} \right )} - \gamma^{P} v^{d}_{0} \\
& \quad  - \gamma^{P}
v^{p}_{0} \cosh{\left (L_{p} \right )} + v^{d}_{0} \sinh{\left (L_{p}
\right )} - v^{p}_{0} \sinh{\left (L_{p} \right )} \big) \\
& \delta = \gamma^{P}
\lambda^{D} \cosh{\left (L_{p} \right )} \cosh{\left (L - L_{p} \right
)} + \gamma^{P} \lambda^{P} \sinh{\left (L_{p} \right )} \sinh{\left
(L - L_{p} \right )}  \\
& \quad + \lambda^{D} \sinh{\left (L_{p} \right )}
\cosh{\left (L - L_{p} \right )}  + \lambda^{P} \sinh{\left (L - L_{p}
\right )} \cosh{\left (L_{p} \right )}
\end{split}
\end{equation}

\section{Membrane potential response to a synaptic event}
\label{sec-3}
\label{sec:eq-for-var-around-mean}

We now look for the response to \(n_{src}= \lfloor \frac{B \,
x_{src}}{l} \rfloor} \) synaptic events at position \(x_{src}\) on all
branches of the generation of \(x_src\), those events have a
conductance $g(t)/n_{src}$ and reversal potential $E_{rev}$. We make
the hypothesis that the initial condition correspond to the stationary
mean membrane potential $\mu_V(x)$. This potential will also be used
to fix the driving force at the synapse to $\mu_v(x_{src})-E_{rev}$,
this linearizes the equation and will allow an analytical
treatment. To derive the equation for the response around the mean
\(\mu_v(x)\), we rewrite Equation 9 in main text with \(v(x, t) =
\delta v(x, t) + \mu_v(x)\), we obtain the equation for \(\delta v(x,
t)\):

\begin{equation}
\label{eq:psp-equation}
\left\{
\begin{split}
& \frac{1}{r_i} \frac{\partial^2 \delta v}{\partial x^2} = 
c_m \frac{\partial \delta v}{\partial t} 
+ \frac{\delta v}{r_m} (1 + r_m \, g_{e0}^p + r_m \, g_{i0}^p) \\
& \qquad - \delta(x-x_{src}) \, \big(\mu_v(x_{src})-E_{rev}\big) \, \frac{g(t)}{n_{src}},
\quad \forall x \in [0,l_p] \\
& \frac{1}{r_i} \frac{\partial^2 \delta v}{\partial x^2} = 
c_m \frac{\partial \delta v}{\partial t} 
+ \frac{\delta v}{r_m} (1 + r_m \, g_{e0}^d + r_m \, g_{i0}^d) \\
& \qquad
- \delta(x-x_{src}) \, \big(\mu_v(x_{src})-E_{rev}\big) \, \frac{g(t)}{n_{src}},
\quad   \forall x \in [l_p,l]\\
& \frac{1}{r_i} \frac{\partial \delta v}{\partial x}_{|x=0} = 
 C_M \frac{\partial \delta  v}{\partial t}_{|x=0} +  
 \frac{ \delta v(0,t)}{R_m} ( 1+ R_m G_{i0}^S) \\
&  \delta v(l_p^-,t) = \delta v(l_p^+,t) \\
& \frac{\partial \delta v}{\partial x}_{l_p^-} 
= \frac{\partial \delta v}{\partial x}_{l_p^+} \\
& \frac{\partial \delta v}{\partial x}_{x=l} = 0
\end{split}
\right.
\end{equation}

Because this synaptic event is concomitant in all branches at distance
$x_{src}$, we can use again the reduction to the equivalent cylinder
(note that the event has now a weight multiplied by $n_{src}$ so that
its conductance becomes \(g(t)\)), we obtain:

\begin{equation}
\label{eq:psp-equation-reduced}
\left\{
\begin{split}
& \frac{\partial^2 \delta v}{\partial X^2} =
\big( \tau_m^p + (\tau_m^d-\tau_m^p) 
\mathcal{H}(X-L_p) \big) \frac{\partial \delta v}{\partial t} + \delta v \\
& \qquad - \big(\mu_v(X_{src})-E_{rev}\big) \,  \delta(X-X_{src}) \times \\
& \qquad \qquad \frac{g(t)}{c_m} 
  \big( \frac{\tau_m^p}{\lambda^p} +
  (\frac{\tau_m^d}{\lambda^d}-\frac{\tau_m^p}{\lambda^p}) 
\mathcal{H}(X_{src}-L_p) \big) \\
& \frac{\partial \delta v}{\partial X}_{|X=0} = 
 \gamma^p \big( \tau_m^S \frac{\partial \delta  v}{\partial t}_{|X=0} +  
 \delta v(0,t) \big) \\
& \delta v(L_p^-,t) = \delta v(L_p^+,t) \\
& \frac{\partial \delta v}{\partial X}_{L_p^-} 
= \frac{\lambda^p}{\lambda^d} \, 
\frac{\partial \delta v}{\partial X}_{L_p^+} \\
& \frac{\partial \delta v}{\partial X}_{X=L} = 0
\end{split}
\right.
\end{equation}

where we have introduced the following time constants:

\begin{equation}
\label{eq:time-constants}
\begin{split}
 & \tau_m^D = \frac{r_m \, c_m}{1+r_m \, g_{e0}^d+r_m \, g_{i0}^d} \\
 & \tau_m^P = \frac{r_m \, c_m}{1+r_m \, g_{e0}^p+r_m \, g_{i0}^p} \\
 & \tau_m^S = \frac{R_m \, C_m}{1+R_m \, G_{i0}^S}
\end{split}
\end{equation}

Now used distribution theory (see \citetext{Appel2008} for a
comprehensive textbook) to translate the synaptic input into boundary
conditions at $X_{src}$, physically this corresponds to: 1) the
continuity of the membrane potential and 2) the discontinuity of the
current resulting from the synaptic input.

\begin{equation}
\left\{
\begin{split}
&  \delta v(X_{src}^-,f) = \delta v(X_{src}^+,f) \\
& \frac{\partial \delta v}{\partial X}_{X_{src}^+} 
- \frac{\partial \delta v}{\partial X}_{X_{src}^-} 
= - \big(\mu_v(X_{src})-E_{rev}\big) \times \\
& \qquad \qquad \qquad 
\big( \frac{\tau_m^p}{\lambda^p} +
  (\frac{\tau_m^d}{\lambda^d}-\frac{\tau_m^p}{\lambda^p}) 
 \mathcal{H}(X_{src}-L_p) \big) \, \frac{g(t)}{c_m} \\
\end{split}
\right.
\end{equation}

We will solve Equation \ref{eq:psp-equation-reduced} by using Fourier
analysis. We take the following convention for the Fourier transform:

\begin{equation}
\label{eq:fourier-convention}
\hat{F}(f) = \int_\mathbb{R} F(t) \, e^{- 2 i \pi f t} \, dt
\end{equation}

We Fourier transform the set of Equations \ref{eq:psp-equation-reduced}, we
obtain:

\begin{equation}
\label{eq:psp-equation-fourier}
\left\{
\begin{split}
& \frac{\partial^2 \hat{\delta v}}{\partial X^2} =
\big( \alpha_f^p + (\alpha_f^d-\alpha_f^p) 
\mathcal{H}(X-L_p) \big)^2 \, 
\hat{\delta v}  \\
& \frac{\partial \hat{\delta v}}{\partial X}_{|X=0} = 
 \gamma_f^p \,  \hat{\delta v}(0,f) \\
&  \hat{\delta v}(X_{src}^-,f) = \hat{\delta v}(X_{src}^+,f) \\
& \frac{\partial \hat{\delta v}}{\partial X}_{X_{src}^-} 
= \frac{\partial \hat{\delta v}}{\partial X}_{X_{src}^+} 
- \big(\mu_v(X_{src})-E_{rev}\big) \times \\
& \qquad \qquad \qquad \qquad 
\big( r_f^p + (r_f^d-r_f^p) \mathcal{H}(X_{src}-L_p) \big) \, \hat{g(f)} \\
& \hat{\delta v}(L_p^-,f) = \hat{\delta v}(L_p^+,f) \\
& \frac{\partial \hat{\delta v}}{\partial X}_{L_p^-} 
= \frac{\lambda^p}{\lambda^d} \, 
\frac{\partial \hat{\delta v}}{\partial X}_{L_p^+} \\
& \frac{\partial \hat{\delta v}}{\partial X}_{X=L} = 0
\end{split}
\right.
\end{equation}

where 
\begin{equation}
\begin{split}
& \alpha_f^p = \sqrt{1+ 2 i \pi f \tau_m^p} \qquad
 r_f^p = \frac{\tau_m^p}{c_m \, \lambda^p} \\
& \alpha_f^d = \sqrt{1+ 2 i \pi f \tau_m^d} \qquad
 r_f^d = \frac{\tau_m^d}{c_m \, \lambda^d} \\
& \qquad \qquad \gamma_f^p =  \gamma^p \, (1+ 2 i \pi f \tau_m^S) \\
\end{split}
\end{equation}

To obtain the solution, we need to split the solution into two cases:

\begin{enumerate}
\item $X_{src} \leq L_p$
\label{sec-3-0-0-1}

Let's write the solution to this equation as the form (already
including the boundary conditions at $X=0$ and $X=L$):

\begin{equation}
\begin{split}
& \hat{\delta v}(X, X_{src}, f) = \\
&\left\{
\begin{split}
& A_f(X_{src}) \, \big ( \cosh(\alpha_f^p \, X)+\gamma^p \, \sinh(\alpha_f^p \, X) \big) \\
& \qquad \qquad \mathrm{ if: } 0 \leq X \leq X_{src} \leq L_p \leq L \\
& B_f(X_{src})\, \cosh(\alpha_f^p \, (X-L_p))+C_f(X_{src})\, \sinh(\alpha_f^p \, (X-L_p)) \\
& \qquad \qquad \mathrm{ if: } 0 \leq X_{src}  \leq X \leq L_p \leq L \\
& D_f(X_{src}) \, \cosh(\alpha_f^d \, (X-L) )  \\
& \qquad \qquad \mathrm{ if: } 0 \leq X_{src} \leq L_p  \leq X \leq L 
\end{split}
\right.
\end{split}
\end{equation}

We write the 4 conditions correspondingto the conditions in $X_{src}$
and $L_p$ to get $A_f, B_f, C_f, D_f$. On a matrix form, this gives:

\begin{equation}
\hspace{-4cm}
\footnotesize
M = 
\begin{pmatrix}
    \cosh(\alpha_f^p \, X_{src})+\gamma_f^p \sinh(\alpha_f^p \, X_{src})  
         & -\cosh(\alpha_f^p \, (X_{src}-L_p)) & -\sinh(\alpha_f^p \, (X_{src}-L_p)) & 0 \\
    \alpha_f^p \big ( \sinh(\alpha_f^p \, X_{src})+\gamma_f^p \cosh(\alpha_f^p \, X_{src})  \big)
         & - \alpha_f^p \sinh(\alpha_f^p \, (X_{src}-L_p)) & -\alpha_f^p \cosh(\alpha_f^p \, (X_{src}-L_p)) & 0 \\
    0 & 1 & 0 & - \cosh(\alpha_f^d \, (L_p-L)) \\
    0 & 0 & \alpha_f^p & -  \alpha_f^d \frac{\lambda^p}{\lambda^d} \, \sinh(\alpha_f^d \, (L_p-L))
\end{pmatrix}
\end{equation}

\begin{equation}
M \cdot
\begin{pmatrix}
    A_f \\
    B_f \\
    C_f \\
    D_f
\end{pmatrix} = 
\begin{pmatrix}
0 \\
- r_f^p I_f \\
0 \\
0
\end{pmatrix}
\end{equation}

And we will solve it with the \texttt{solve\_linear\_system\_LU} method of
\texttt{sympy}. For the $A_f(X_{src})$ coefficient, we obtain:

\begin{equation}
A_f(X_{src}) = \frac{a^1_f(X_{src})}{a^2_f(X_{src})}
\end{equation}

with:

\begin{equation}
\begin{split}
& a^1_f(X_{src}) = I_{f} r^{P}_{f} \left(- \alpha^{D}_{f} \lambda^{P} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} - L_{p} \alpha^{P}_{f} + X_{s} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{D}_{f} \lambda^{P} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} - X_{s} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{P}_{f} \lambda^{D} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} - L_{p} \alpha^{P}_{f} + X_{s} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{P}_{f} \lambda^{D} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} - X_{s} \alpha^{P}_{f} \right )}\right)\\
& a^2_f(X_{src}) = \alpha^{P}_{f} \left(- \alpha^{D}_{f} \gamma^{P}_{f} \lambda^{P} \cosh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{D}_{f} \gamma^{P}_{f} \lambda^{P} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )} -  \\
& \qquad \alpha^{D}_{f} \lambda^{P} \sinh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{D}_{f} \lambda^{P} \sinh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{P}_{f} \gamma^{P}_{f} \lambda^{D} \cosh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{P}_{f} \gamma^{P}_{f} \lambda^{D} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{P}_{f} \lambda^{D} \sinh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad + \alpha^{P}_{f} \lambda^{D} \sinh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}\right)\\
\end{split}
\end{equation}

\item \$ L$_{\text{p}}$ $\le$ X$_{\text{src}}$\$
\label{sec-3-0-0-2}

Let's write the solution to this equation as the form (already
including the boundary conditions at $X=0$ and $X=L$:

\begin{equation}
\begin{split}
& \hat{\delta v}(X, X_{src}, f) = \\
&\left\{
\begin{split}
& E_f(X_{src}) \, \big ( \cosh(\alpha_f^p \, X)+\gamma^p \, \sinh(\alpha_f^p \, X) \big) \\
& \qquad \qquad \mathrm{ if: } 0 \leq X \leq L_p \leq X_{src} \leq L \\
& F_f(X_{src})\, \cosh(\alpha_f^d \, (X-L_p))+G_f(X_{src})\, \sinh(\alpha_f^d \, (X-L_p)) \\
& \qquad \qquad \mathrm{ if: } 0  \leq L_p  \leq X \leq X_{src} \leq L \\
& H_f(X_{src}) \, \cosh(\alpha_f^d \, (X-L) )  \\
& \qquad \qquad \mathrm{ if: } 0  \leq L_p \leq X_{src}  \leq X \leq L 
\end{split}
\right.
\end{split}
\end{equation}

We write the 4 conditions correspondingto the conditions in $X_{src}$
and $L_p$ to get $A_f, B_f, C_f, D_f$. On a matrix form, this gives:

We rewrite this condition on a matrix form:

\begin{equation}
\hspace{-4cm}
\footnotesize
M_2 = 
\begin{pmatrix}
    \cosh(\alpha_f^p \, L_p)+\gamma_f^p \sinh(\alpha_f^p \, L_p) & -1 & 0 &0 & 0 \\
    \alpha_f^p \big ( \sinh(\alpha_f^p \, L_p)+\gamma_f^p \cosh(\alpha_f^p \, L_p)  \big) 
         & 0 & -  \alpha_f^d \frac{\lambda^p}{\lambda^d} & 0 \\
    0 & \cosh(\alpha_f^d \, (X_{src}-L_p)) & \sinh(\alpha_f^d \, (X_{src}-L_p)) & - \cosh(\alpha_f^d \, (X_{src}-L))\\
    0 & \alpha_f^d \, \sinh(\alpha_f^d \, (X_{src}-L_p)) & \alpha_f^d \, \cosh(\alpha_f^d \, (X_{src}-L_p))
         & - \alpha_f^d \, \sinh(\alpha_f^d \, (X_{src}-L))\\
\end{pmatrix}
\end{equation}

\begin{equation}
M \cdot
\begin{pmatrix}
    E_f \\
    F_f \\
    G_f \\
    H_f
\end{pmatrix} = 
\begin{pmatrix}
0 \\
0 \\
0 \\
- r_f^d I_f
\end{pmatrix}
\end{equation}

And we will solve it with the \texttt{solve\_linear\_system\_LU} method of
\texttt{sympy}. For the $E_f(X_{src})$ coefficient, we obtain:

\begin{equation}
E_f(X_{src}) = \frac{e^1_f(X_{src})}{e^2_f(X_{src})}
\end{equation}

with:

\begin{equation}
\begin{split}
& e^1_f(X_{src}) = 2 I_{f} \lambda^{P} r^{D}_{f} \cosh{\left (\alpha^{D}_{f} \left(L - X_{s}\right) \right )} \\
& e^2_f(X_{src}) = - \alpha^{D}_{f} \gamma^{P}_{f} \lambda^{P} \cosh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )} \\
& \qquad + \alpha^{D}_{f} \gamma^{P}_{f} \lambda^{P} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad- \alpha^{D}_{f} \lambda^{P} \sinh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad+ \alpha^{D}_{f} \lambda^{P} \sinh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad+ \alpha^{P}_{f} \gamma^{P}_{f} \lambda^{D} \cosh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad+ \alpha^{P}_{f} \gamma^{P}_{f} \lambda^{D} \cosh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad+ \alpha^{P}_{f} \lambda^{D} \sinh{\left (- L \alpha^{D}_{f} + L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}  \\
& \qquad+ \alpha^{P}_{f} \lambda^{D} \sinh{\left (L \alpha^{D}_{f} - L_{p} \alpha^{D}_{f} + L_{p} \alpha^{P}_{f} \right )}
\end{split}
\end{equation}

\item PSP at the soma
\label{sec-3-0-0-3}

The main text writes a solution for the PSP at soma of the form:

\begin{equation}
\hat{\delta v}(X=0, X_{src}, f) = K_f(X_{src}) \, 
\big(\mu_v(X_{src})-E_{rev}\big) \,  \hat{g(f)} 
\end{equation}

The correspondance with the previous calculus is to take a unitary
current \(I_f=1\) and \( K_f(X_{src}) \) given by:

\begin{equation}
K_f(X_{src}) = 
\left\{
\begin{split}
& A_f(X_{src}) \forall X_{src} \in [0,L_p] \\
& E_f(X_{src}) \forall X_{src} \in [L_p, L]
\end{split}
\right.
\end{equation}
\end{enumerate}

\section{Deriving the fluctuations properties}
\label{sec-4}

From shotnoise theory \cite{Daley2007} (see also
\citetext{ElBoustani2009a} for an application similar to ours), we can
obtain the power spectral density of the V$_{\text{m}}$ fluctuations \( P_V(f) \)
as a response to the stimulation Equation \texttt{eq:fluct-eq}:

\begin{equation}
\label{eq:vm-pwd}
 P_V(f)  = & \sum_{syn} \pi \mathcal{D}_{syn}  \nu_{syn} \, \| \hat{\mathrm{PSP}}(f) \|^2 
\end{split}
\end{equation}

\begin{equation}
\label{eq:Tv-def-with-pwd}
  \tau_V = \frac{1}{2} \, \big( \frac{\int_\mathbb{R} P_V(f) \, d f}{ P_V(0) } \big)^{-1}
\end{equation}

\begin{equation}
\label{eq:var-expr}
  \sigma_V^2 = \int_\mathbb{R} P_V(f) \, df
\end{equation}

\section{References}
\label{sec-5}
\bibliography{biblio}
% Emacs 24.5.1 (Org mode 8.2.10)
\end{document}

### 2016-06-19 derivation_supplementary/supplementary.tex
up supp

@@
 \usepackage[T1]{fontenc}
-\usepackage{fixltx2e}
-\usepackage{graphicx}
-\usepackage{longtable}
-\usepackage{float}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{textcomp}
-\usepackage{marvosym}
-\usepackage{wasysym}
-\usepackage{amssymb}
+\usepackage{amsmath, amssymb}
 \usepackage{hyperref}
-\tolerance=1000
+%% \tolerance=1000
 \hypersetup{allcolors = blue} % to have all the hyperlinks in 1 color
@@
 \title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}}
-\hypersetup{
-  pdfkeywords={},
-  pdfsubject={},
-  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
 \begin{document}
@@
 \quad 
-\lambda^d= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^d + r_m g_{i0}^d)}}$
+\lambda^d= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^d + r_m g_{i0}^d)}}
 \end{equation}
@@
 
-Now used distribution theory (see \citetext{Appel2008} for a
+We now use distribution theory (see \citetext{Appel2008} for a
 comprehensive textbook) to translate the synaptic input into boundary
@@
 
-\item \$ L$_{\text{p}}$ $\le$ X$_{\text{src}}$\$
+\item $ L_p \le X_{\text{src}}$
 \label{sec-3-0-0-2}
@@
 \begin{split}
-& A_f(X_{src}) \forall X_{src} \in [0,L_p] \\
-& E_f(X_{src}) \forall X_{src} \in [L_p, L]
+& A_f(X_{src}) \quad \forall X_{src} \in [0,L_p] \\
+& E_f(X_{src}) \quad \forall X_{src} \in [L_p, L]
 \end{split}
@@
 
-\section{Deriving the fluctuations properties}
+\section{Deriving the power spectrum of the membrane potential fluctuations}
 \label{sec-4}
 
-From shotnoise theory \cite{Daley2007} (see also
-\citetext{ElBoustani2009a} for an application similar to ours), we can
-obtain the power spectral density of the V$_{\text{m}}$ fluctuations \( P_V(f) \)
-as a response to the stimulation Equation \texttt{eq:fluct-eq}:
+The calculus rely on the ability to obtain the power spectrum of the
+membrane potential fluctuations at the soma $P_V(f)$.
+
+This can be obtained from shotnoise theory \cite{Daley2007} (see also
+\citetext{ElBoustani2009a} for an application similar to ours), the
+general form can be expressed as:
 
@@
 \label{eq:vm-pwd}
- P_V(f)  = & \sum_{syn} \pi \mathcal{D}_{syn}  \nu_{syn} \, \| \hat{\mathrm{PSP}}(f) \|^2 
+P_V(f)  = \sum_{\{syn\}} N_{syn} \,  F_\mathrm{synch} \, \nu_{syn}
+\, \| \hat{\mathrm{PSP}_{syn}}(f) \|^2 
 \end{split}
 \end{equation}
+
+where $\{syn\}$ is the set of identical synapses, each having
+$N_{syn}$ synapses, a Poisson release probability: $\nu_{syn}$ and
+creating a post-synaptic event $\mathrm{PSP}_{syn}(t)$.
+
+In addition, we added a synchrony factor $F_\mathrm{synch}$ that
+accounts for the effects of the synchronous arrivals of presynaptic
+events. Given the synchrony generator considered in the main text, the
+synchrony factor takes the form:
+
+\begin{equation}
+\label{eq:F-synch}
+F_\mathrm{synch} =(1-s) + (s-s^2) 2^2 + (s^2-s^3) 3^2 + s^3 4^2
+\end{split}
+\end{equation}
+
+because single events arise with a probability $1-s$, double events
+with a probability $s-s^2$ (and the PSP are squared in
+Eq. \ref{eq:vm-pwd}, hence the $2^2$ factor), etc...
+
+\section{Deriving the fluctuations properties}
+\label{sec-5}
 
@@
 \bibliography{biblio}
-% Emacs 24.5.1 (Org mode 8.2.10)
+
 \end{document}

### 2016-06-20 derivation_supplementary/supplementary.tex
finished with the supplementary derivation

@@
 \right.
+\label{eq:1}
 \end{equation}
@@
 \begin{equation}
+ X(x) = \int_0^x \frac{dx}{\lambda(x)}
 \label{eq:x-rescale}
- X(x) = \int_0^x \frac{dx}{\lambda(x)}
 \end{equation}
@@
 \right.
+\label{eq:muV-final}
 \end{equation}
@@
 
-\item PSP at the soma
-\label{sec-3-0-0-3}
-
-The main text writes a solution for the PSP at soma of the form:
+From this calculus, we can write the PSP at the soma on the form:
 
 \begin{equation}
+\label{eq:delta-v-final}
 \hat{\delta v}(X=0, X_{src}, f) = K_f(X_{src}) \, 
@@
 
-The correspondance with the previous calculus is to take a unitary
-current \(I_f=1\) and \( K_f(X_{src}) \) given by:
+where \( K_f(X_{src}) \) given by:
 
@@
 
+This is obtained by taking a unitary current \(I_f=1\) in the previous calculus.
+
 \section{Deriving the power spectrum of the membrane potential fluctuations}
@@
 \citetext{ElBoustani2009a} for an application similar to ours), the
-general form can be expressed as:
+general form of the power spectrum density can be expressed as:
 
 \begin{equation}
-\label{eq:vm-pwd}
 P_V(f)  = \sum_{\{syn\}} N_{syn} \,  F_\mathrm{synch} \, \nu_{syn}
@@
 \end{split}
+\label{eq:vm-pwd}
 \end{equation}
@@
 $N_{syn}$ synapses, a Poisson release probability: $\nu_{syn}$ and
-creating a post-synaptic event $\mathrm{PSP}_{syn}(t)$.
-
-In addition, we added a synchrony factor $F_\mathrm{synch}$ that
-accounts for the effects of the synchronous arrivals of presynaptic
-events. Given the synchrony generator considered in the main text, the
-synchrony factor takes the form:
+creating a post-synaptic event $\mathrm{PSP}_{syn}(t)$. In addition,
+$F_\mathrm{synch}$ is a synchrony factor (depending on the variable
+$s$ in the model), it accounts for the effects of the synchronous
+arrivals of presynaptic events. Given the synchrony generator
+considered in the main text, the synchrony factor takes the form:
 
@@
 
-\section{Deriving the fluctuations properties}
+Now obtaining the power spectrum density $P_V(f)$ in our situation
+requires to explicit the sum over synapses: $\sum_{\{syn\}}$, In our
+cases, we need to sum over 1) their type (excitatory/inhibitory,
+$\sum_{s \in \{e,i\}}$ ), 2) their location (we will integrate over
+the dendritic length $\int_0^L dx$) 3) branches.
+
+\begin{equation}
+\begin{split}
+  P_V(f)  = & \sum_{s \in \{e,i\}} \int_0^L \, dx \,  \pi \, \mathcal{D}_s
+  \Big( d_t \, 2^{- \frac{2}{3} \, \lfloor \frac{B \, x}{l} \rfloor} \Big)
+  \, \,  2^{\lfloor \frac{B \, x}{l} \rfloor} \, \, \,  F_\mathrm{synch} \, \nu_{s}(x)
+  \, \| \hat{\delta v}_{s}(0, x, f) \|^2 \\
+  & + \pi \, \mathcal{D}_i \, l_{S} \, d_{S} \, \,  F_\mathrm{synch} \, \nu_{i}(0)
+  \, \| \hat{\delta v}_{i}(0, 0, f) \|^2 
+\end{split}
+\label{eq:vm-pwd-final}
+\end{equation}
+
+where $ \hat{\delta v}_{s}(0, x, f)$ is given by
+Eq. \ref{eq:delta-v-final} (note that the dependency on synaptic type
+$s$ comes from the reversal potential term $E_{rev}$ in
+Eq. \ref{eq:delta-v-final}). The factor $2^{\lfloor \frac{B \, x}{l}
+  \rfloor}$ corresponds to the sum of the synapses over the different
+branches at the distance $x$. The term $\big( d_t \, 2^{- \frac{2}{3}
+  \, \lfloor \frac{B \, x}{l} \rfloor} \Big)$ is the diameter of the
+branches at the distance $x$.
+
+The last term in Eq. \ref{eq:vm-pwd-final} corresponds to the
+contribution of somatic inhibitory synapses (number of somatic
+inhibitory synapses: $\pi \, \mathcal{D}_i \, l_{S} \, d_{S}$.
+
+\section{Deriving the fluctuations properties ($\mu_V, \sigma_V, \tau_V$)}
 \label{sec-5}
+
+The final expressions for the fluctuation propeorties as a function of
+($\nu_e^p, \nu_i^p, \nu_e^d, \nu_i^d, s$) are thus given by:
+
+\begin{itemize}
+
+  \item $\mu_V$: we obtain the mean of the fluctuations at the soma by
+    taking $\mu_V(0)$ in Equation \ref{eq:muV-final}.
+
+  \item $\sigma_V$: we obtain the standard deviation of the fluctuations from the power spectrum density in Equation \ref{eq:vm-pwd-final} and the expression:
+
+    \begin{equation}
+      \label{eq:var-expr}
+      \sigma_V^2 = \int_\mathbb{R} P_V(f) \, df
+    \end{equation}
+
+    This integral expression was discretized and evaluated numerically
+
+  \item $\tau_V$: we obtain the autocorrelation time of the
+    fluctuations from the power spectrum density in Equation
+    \ref{eq:vm-pwd-final} and the expression \cite{Zerlaut2016}:
 
@@
 
-\begin{equation}
-\label{eq:var-expr}
-  \sigma_V^2 = \int_\mathbb{R} P_V(f) \, df
-\end{equation}
+    This integral expression was discretized and evaluated numerically
+
+\end{itemize}
 

### 2016-08-04 derivation_supplementary/supplementary.tex
adding larkum et al. morphology and mechanisms

@@
 \date{\today}
-\title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}}
+\title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in mice layer V pyramidal neurons}}
 \begin{document}

### 2016-08-04 numerical_simulations/nrn_simulations.py

@@ -1,4 +1,9 @@
 # nrn_simulations.py
+import platform, sys
+if platform.system()=='Darwin':
+    sys.path.append('/Applications/NEURON-7.4/nrn/lib/python')
+    sys.path.append('/System/Library/Frameworks/Python.framework/Versions/2.7')
+    sys.path.append('/System/Library/Frameworks/Python.framework/Versions/2.7/lib')
 from neuron import h as nrn
 nrn('objref nil') # need a nil object in NEURON
 import numpy as np

### 2016-08-04 theory/analytical_calculus.py

@@ -1,4 +1,4 @@
-from numba import jit
+# from numba import jit
 import numpy as np
 import matplotlib
 import matplotlib.pylab as plt
@@ -177,22 +177,22 @@ def stat_pot_function(x, shtn_input, soma, stick, params):
     return np.array([muV_prox(XX, Lp, L, lbdD, lbdP, gP, v0D, v0P, V0) if XX<Lp\
                      else muV_dist(XX, Lp, L, lbdD, lbdP, gP, v0D, v0P, V0) for XX in X])
 
-@jit
+# @jit
 def exp_FT(f, Q, Tsyn, t0=0):
     return Q*np.exp(-1j*2*np.pi*t0*f)/(1j*2*np.pi*f+1./Tsyn)
 
-@jit
+# @jit
 def exp_FT_mod(f, Q, Tsyn):
     return Q**2/((2*np.pi*f)**2+(1./Tsyn)**2)
 
-@jit
+# @jit
 def split_root_square_of_imaginary(f, tau):
     # returns the ral and imaginary part of Sqrt(1+2*Pi*f*tau)
     af = np.sqrt((np.sqrt(1+(2*np.pi*f*tau)**2)+1)/2)
     bf = np.sqrt((np.sqrt(1+(2*np.pi*f*tau)**2)-1)/2)
     return af, bf
 
-@jit
+# @jit
 def psp_norm_square_integral_per_dend_synapse_type(x_dest, x_src, f, Gf2,\
                             Erev, shtn_input,\
                             soma, stick, params,
@@ -230,7 +230,7 @@ def psp_norm_square_integral_per_dend_synapse_type(x_dest, x_src, f, Gf2,\
             PSP = dv_Lp_Xsrc_X(Xdest, Xsrc, 1., afP, afD, gfP, rfP, rfD, Lp, L, lbdD, lbdP)
     return Gf2*np.abs(PSP)**2*(Erev-muV_X)**2
 
-# @jit
+# # @jit
 def get_the_theoretical_sV_and_Tv(shtn_input,\
                                   f, x, params, soma, stick,\
                                   precision=50):
@@ -314,7 +314,7 @@ def get_the_theoretical_sV_and_Tv(shtn_input,\
         
     return np.sqrt(sV2), Tv
 
-@jit
+# @jit
 def psp_norm_square_integral_per_dend_synapse_type_at_soma(x_src, f, Gf2,\
                             Erev, shtn_input,\
[…]

### 2016-09-19 input_impedance_calibration/larkum_minimization.py
working minimization and starting transfer impedance check

@@ -15,15 +15,15 @@ f, psd_means, phase_means = np.load('../larkumEtAl2009/data/larkum_imped_data.np
 phase_means = -phase_means
 
 #### ================================================== ##
-#### MODEL VARIATIONS ###############################
+#### ####### MODEL VARIATIONS ############################
 #### ================================================== ##
 
 N0, N = 5, 5
 B = np.arange(N)+N0 # to be adjusted !!! (does not depends on N)
 L_soma = np.linspace(5., 60., N)*1e-6
 L_dend = np.linspace(700., 1200., N)*1e-6
-D_dend = np.linspace(2, 6., N)*1e-6
-G_PAS = np.linspace(1e-4, 1e-2, N)*1e4
+D_dend = np.linspace(3., 7., N)*1e-6
+G_PAS = np.linspace(17e-5, 3e-5, N)*1e4
 CM = np.linspace(.8, 1.8, N)*1e-2
 RA = np.linspace(10., 90., N)*1e-2
 

### 2016-09-19 input_impedance_calibration/look_at_transfer_resist_histograms.py

@@ -1,8 +1,8 @@
 import numpy as np
 import matplotlib.pylab as plt
 import sys
-sys.path.append('/home/yann/work/python_library')
-from my_graph import set_plot
+sys.path.append('/Users/yzerlaut/work/common_libraries/')
+from graphs.my_graph import set_plot
 sys.path.append('../')
 from theory.analytical_calculus import *
 from data_firing_response.analyze_data import get_Rm_range

### 2016-09-19 coupling_model/firing_responses.py
adding the file for the prox/dist study asked by the reviewer

@@ -35,14 +35,14 @@ if __name__=='__main__':
                  
     FIG_LIST = []
     if sys.argv[-1]=='all':
-        CHOOSED_CELLS = range(len(ALL_CELLS))
+        CHOOSED_CELLS = list(range(len(ALL_CELLS)))
     else:
         CHOOSED_CELLS = [0, 2, 27, 1]
     ii=1
     for i_nrn in CHOOSED_CELLS:
         fig, ax = plt.subplots(figsize=(4, 3))
         plt.subplots_adjust(left=.3, bottom=.3, wspace=.2, hspace=.2)
-        print 'cell : ', i_nrn+1
+        print('cell : ', i_nrn+1)
         ax.set_title('cell'+str(i_nrn+1))
         for protocol, c in zip(PROTOCOLS, COLORS[:5]):
             Fout = single_experiment(i_nrn, exp_type=protocol, len_f=len_f, precision=1e3)

### 2016-09-19 coupling_model/nice_plot.py

@@ -30,7 +30,7 @@ VTHREs, DMUVs, DTSVs, DTVs = VTHRE[INDEXES], DMUV[INDEXES], DTSV[INDEXES], DTV[I
 cond = (NU0>0)# to have all cells !!
 cond = (NU0>1e-4)
 np.save('kept_cells.npy', cond)
-print 'number of kept cells:',  len(NU0[cond])
+print('number of kept cells:',  len(NU0[cond]))
 NU0, NU, UNBALANCED, PROX, DIST, SYNCH = NU0[cond], NU[cond], UNBALANCED[cond], PROX[cond], DIST[cond], SYNCH[cond]
 VTHRE, DMUV, DTSV, DTV = VTHRE[cond], DMUV[cond], DTSV[cond], DTV[cond]
 

### 2016-09-19 coupling_model/population_coupling.py

@@ -91,18 +91,18 @@ def make_fig(args):
                run_single_experiment(t, int(NEURONS[i_nrn]),\
                         args, exp_type=PROTOCOLS[ip], seed=SEEDS[ip])
     ### PLOTTING ALL
-    for ip, color in zip(range(len(PROTOCOLS)), COLORS):
+    for ip, color in zip(list(range(len(PROTOCOLS))), COLORS):
         # membrane potential quantities
-        for j, x in zip(range(4), [1e3*MUV[ip,1,:], 1e3*SV[ip,1,:],\
+        for j, x in zip(list(range(4)), [1e3*MUV[ip,1,:], 1e3*SV[ip,1,:],\
                     1e2*TVN[ip,1,:], MUGN[ip,1,:]]):
             AX1[j, ip].plot(t, x, color=color, lw=3, label=PROTOCOLS[ip])
-        for j, x in zip(range(4), [1e3*MUV[ip,0,:], 1e3*SV[ip,0,:],\
+        for j, x in zip(list(range(4)), [1e3*MUV[ip,0,:], 1e3*SV[ip,0,:],\
                     1e2*TVN[ip,0,:], MUGN[ip,0,:]]):
             AX1[j, ip].plot(t, x, 'k-', lw=1, label='non specific activity')
         # presynaptic activity
-        for j, x in zip(range(4), [FEG[ip,1,:], FIG[ip,1,:], FEI[ip,1,:], FII[ip,1,:]]):
+        for j, x in zip(list(range(4)), [FEG[ip,1,:], FIG[ip,1,:], FEI[ip,1,:], FII[ip,1,:]]):
             AX2[j, ip].plot(t, x, color=color, lw=3, label=PROTOCOLS[ip])
-        for j, x in zip(range(4), [FEG[ip,0,:], FIG[ip,0,:], FEI[ip,0,:], FII[ip,0,:]]):
+        for j, x in zip(list(range(4)), [FEG[ip,0,:], FIG[ip,0,:], FEI[ip,0,:], FII[ip,0,:]]):
             AX2[j, ip].plot(t, x, 'k-', lw=1, label='non specific activity')
         # then output firing
         for i_nrn in range(len(NEURONS)):
@@ -111,9 +111,9 @@ def make_fig(args):
             
     # THEN LIMITS
     for ip in range(len(PROTOCOLS)):
-        for j, x in zip(range(4), [FEG, FIG, FEI, FII]):
+        for j, x in zip(list(range(4)), [FEG, FIG, FEI, FII]):
[…]

### 2016-09-19 coupling_model/simple_coupling.py

@@ -29,7 +29,7 @@ def single_experiment(i_nrn, balance=-54e-3):
     COLORS=['r', 'b', 'g', 'c']
 
     ii=0
-    for p, i  in zip(PROTOCOLS, range(2,len(coupling))):
+    for p, i  in zip(PROTOCOLS, list(range(2,len(coupling)))):
         feG, fiG, feI, fiI, synch, muV, sV, TvN, muGn = get_fluct_var(i_nrn, exp_type=p, balance=balance)
         Fout2 = final_func(ALL_CELLS[i_nrn]['P'], muV, sV, TvN,\
                            ALL_CELLS[i_nrn]['Gl'], ALL_CELLS[i_nrn]['Cm'])
@@ -116,7 +116,7 @@ if __name__=='__main__':
         COUPLINGS = np.zeros((6, len(ALL_CELLS)))
         BIOPHYSICS = np.zeros((4, len(ALL_CELLS)))
         for i_nrn in range(len(ALL_CELLS)):
-            print 'cell', i_nrn
+            print('cell', i_nrn)
             BIOPHYSICS[:,i_nrn] = ALL_CELLS[i_nrn]['E']
             COUPLINGS[:,i_nrn] = single_experiment(i_nrn)
         np.save('data/elctrophy_vs_coupling.npy', [COUPLINGS, BIOPHYSICS])

### 2016-09-19 coupling_model/synaptic_integration.py

@@ -45,9 +45,9 @@ def get_fluct_var(i_nrn, F=None, exp_type='non specific activity', balance=-54e-
         feG, fiG, feI, fiI = F, inh_factor*F, F, inh_factor*F
         fiG, fiI = find_inh_cond_for_balance(feG, fiG, feI, fiI, fe0,i_nrn, balance+0*F)
     else:
-        print '------------------------------------------'
-        print 'problem with the protocol: ', exp_type
-        print '------------------------------------------'
+        print('------------------------------------------')
+        print('problem with the protocol: ', exp_type)
+        print('------------------------------------------')
 
     shtn_input = {'fi_soma':fiG, 'fe_prox':feG+fe0,'fi_prox':fiG,
                   'fe_dist':feI+fe0,'fi_dist':fiI, 'synchrony':synch+0.*F}
@@ -92,7 +92,7 @@ if __name__=='__main__':
                [np.zeros((len(ALL_CELLS), len(F))) for j in range(10)]
 
             for i_nrn in range(len(ALL_CELLS)):
-                print 'cell: ', i_nrn
+                print('cell: ', i_nrn)
                 FEG[i_nrn,:], FIG[i_nrn,:], FEI[i_nrn,:], FII[i_nrn,:], SYNCH[i_nrn,:],\
                    MUV[i_nrn,:], SV[i_nrn,:], TVN[i_nrn,:], MUGN[i_nrn,:] =\
                    get_fluct_var(i_nrn, exp_type=PROTOCOLS[i], len_f=len_f)

### 2016-09-19 input_impedance_calibration/get_calib_larkum.py

@@ -11,17 +11,12 @@ from theory.analytical_calculus import * # where the core calculus lies
 #### MEAN MODEL PROPERTIES ###############################
 #### ================================================== ##
 
-soma, stick, params = np.load('../input_impedance_calibration/mean_model.npy')
-try:
-    kept_cells = np.load('../coupling_model/kept_cells.npy')
-except IOError:
-    kept_cells = [True for i in range(30)]
-
-
+soma, stick, params = np.load('mean_model_larkum.npy')
 # common to all plots, the frequency range we will look at [0.1,1000] Hz
 dt, tstop = 1.3e-3, 10.
 t = np.arange(int(tstop/dt))*dt
 f = rfft.time_to_freq(len(t), dt)
+f, psd_means, phase_means = np.load('../larkumEtAl2009/data/larkum_imped_data.npy')
 
 def get_input_imped(soma, stick, params):
     # branching properties
@@ -30,228 +25,92 @@ def get_input_imped(soma, stick, params):
     psd, phase = np.abs(output)/1e6, (np.angle(output)+np.pi)%(2.*np.pi)-np.pi
     return psd, phase
 
-def get_input_resist(soma, stick, params):
-    # branching properties
-    params_for_cable_theory(stick, params) # setting cable membrane constants
-    return np.abs(get_the_input_impedance_at_soma(0., soma, stick, params))
-
-def adjust_model_prop(Rm, soma, stick, precision=.5, params2=None, maxiter=1000):
-    """ Rm in Mohm !! """
-    if Rm>1200 or Rm<100:
-        print('---------------------------------------------------')
-        print('/!\ Rm value too high or too low for the conversion')
-        print('---------------------------------------------------')
-
-    # comodulation values :
-    L_soma_base = 2e-6
-    L_dend_base = 150e-6
-    D_dend_base = .8*1e-6
-
-    def get_Rm_from_factor(b):
-        soma1, stick1 = soma.copy(), stick.copy()
-        if params2 is None:
-            params1 = params.copy()
-        else:
-            params1=params2
-        soma1['L'] += b*L_soma_base
-        stick1['L'] += b*L_dend_base
-        stick1['D'] += b*D_dend_base
[…]

### 2016-09-19 input_impedance_calibration/larkum_minimization.py

@@ -18,14 +18,23 @@ phase_means = -phase_means
 #### ####### MODEL VARIATIONS ############################
 #### ================================================== ##
 
-N0, N = 5, 5
+N0, N = 10, 10
 B = np.arange(N)+N0 # to be adjusted !!! (does not depends on N)
-L_soma = np.linspace(5., 60., N)*1e-6
-L_dend = np.linspace(700., 1200., N)*1e-6
-D_dend = np.linspace(3., 7., N)*1e-6
-G_PAS = np.linspace(17e-5, 3e-5, N)*1e4
-CM = np.linspace(.8, 1.8, N)*1e-2
-RA = np.linspace(10., 90., N)*1e-2
+L_soma = np.linspace(20., 1500., 1)*1e-6
+L_dend = np.linspace(900., 1200., 1)*1e-6
+D_dend = np.linspace(1., 10., 1)*1e-6
+G_PAS = np.linspace(5e-5, 30e-5, 1)*1e4
+CM = np.linspace(1., 1., 1)*1e-2
+RA = np.linspace(50., 100., N)*1e-2
+
+# N0, N = 5, 5
+# B = np.arange(N)+N0 # to be adjusted !!! (does not depends on N)
+# L_soma = np.linspace(5., 60., N)*1e-6
+# L_dend = np.linspace(700., 1200., N)*1e-6
+# D_dend = np.linspace(2, 6., N)*1e-6
+# G_PAS = np.linspace(1e-4, 1e-2, N)*1e4
+# CM = np.linspace(.8, 1.8, N)*1e-2
+# RA = np.linspace(10., 90., N)*1e-2
 
 #### ================================================== ##
 #### MODEL PROPERTIES ###############################
@@ -36,11 +45,11 @@ def get_input_imped(soma, stick, params):
     # branching properties
     params_for_cable_theory(stick, params) # setting cable membrane constants
     output = get_the_input_impedance_at_soma(f, soma, stick, params)
-    psd, phase = np.abs(output)/1e6, (np.angle(output)+np.pi/2.)%(2.*np.pi)-np.pi/2.
+    psd, phase = np.abs(output)/1e6, (np.angle(output)+np.pi)%(2.*np.pi)-np.pi
     return psd, -phase
 
 import itertools
-def compute_deviations(factor_for_phase=3.):
+def compute_deviations(factor_for_phase=1.):
     VALUE_PSD, VALUE_PHASE = [], []
     # product loop
[…]

### 2016-09-19 input_impedance_calibration/look_at_transfer_resist_histograms.py

@@ -10,7 +10,6 @@ from input_impedance_calibration.get_calib import adjust_model_prop
 
 # loading mean model
 soma, stick, params = np.load('../input_impedance_calibration/mean_model.npy')
-
 CELLS = np.load('../data_firing_response/reduced_data.npy')
 
 Rtf_model = np.zeros(len(CELLS))
@@ -19,16 +18,27 @@ Rm_data =  np.zeros(len(CELLS))
 fig, ax = plt.subplots(figsize=(4,3))
 plt.subplots_adjust(bottom=.3, left=.3)
 
-for i in range(len(CELLS))[::5]:
-    
-    Rm_data[i] = 1e-6/CELLS[i]['Gl']
-    soma1, stick1, params1 = adjust_model_prop(Rm_data[i], soma, stick)
-    
-    Rtf_model, N_synapses = get_the_transfer_resistance_to_soma(soma1, stick1, params1)
+if sys.argv[-1]=='all':
+    for i in range(len(CELLS))[::5]:
+        Rm_data[i] = 1e-6/CELLS[i]['Gl']
+        soma1, stick1, params1 = adjust_model_prop(Rm_data[i], soma, stick)
+        Rtf_model, N_synapses = get_the_transfer_resistance_to_soma(soma1,\
+                                                                    stick1, params1)
 
-    ax.hist(1e-6*Rtf_model, label='cell'+str(i))
+        ax.hist(1e-6*Rtf_model, label='cell'+str(i))
+
+    ax.legend(frameon=False, prop={'size':'x-small'}, loc='best')
+    set_plot(ax, xlabel='transfer resistance \n to soma $(M \Omega)$',\
+             ylabel='synapses #')
+else:
+    for freq in [0.,2.,10.]:
+        TF_model, Area = get_the_transfer_resistance_to_soma(soma, stick, params, precision=1000, with_area=True, freq=freq)
+        edges, bins = np.histogram(1e-6*TF_model, bins=30, weights=Area, normed=True)
+        bins = .5*(bins[:-1]+bins[1:])
+        plt.bar(bins, edges/edges.max(), width=bins[1]-bins[0], edgecolor='k', lw=0, color='lightgray')
     
-ax.legend(frameon=False, prop={'size':'x-small'}, loc='best')
-set_plot(ax, xlabel='transfer resistance \n to soma $(M \Omega)$', ylabel='synapses #')
[…]

### 2016-09-19 larkumEtAl2009/transfer_resistance_hist.py

@@ -13,11 +13,11 @@ Z.loc(0.5)
 R_transfer, Areas = [], []
 for sec in nrn.allsec():
     for seg in sec.allseg():
-        Z.compute(0 , 0.5)
+        Z.compute(0, seg.x, sec=sec)
         Areas.append(seg.area())
-        R_transfer.append(Z.input(seg.x, sec=sec))
+        R_transfer.append(Z.transfer(seg.x, sec=sec))
 
-edges, bins = np.histogram(R_transfer, bins=50, weights=Areas)
+edges, bins = np.histogram(R_transfer, bins=50, weights=Areas, normed=True)
 plt.bar(bins[:-1], edges, width=bins[1]-bins[0])
 
 np.savez('data/larkum_Tf_Resist_data.npz', R_transfer=R_transfer, Areas=Areas)

### 2016-09-19 theory/analytical_calculus.py

@@ -148,6 +148,7 @@ def rescale_x(x, l, lp, B, lbdP, lbdD):
     # specific to evenly space branches !! (see older implementation with EqCylinder for more general implement.)
     EqCylinder = np.linspace(0, l, B+1)
     C = EqCylinder[EqCylinder<=x]
+    # print(lbd(C[-1], l, lp, B, lbdP, lbdD), lp)
     return np.sum(np.diff(C)/lbd(C, l, lp, B, lbdP, lbdD)[:-1])+(x-C[-1])/lbd(C[-1], l, lp, B, lbdP, lbdD)
 
 def stat_pot_function(x, shtn_input, soma, stick, params):
@@ -464,7 +465,60 @@ def get_the_input_resistance_at_soma(soma, stick, params, shtn_input):
     # input and recording in x=0 
     return np.abs(dv_X_Xsrc_Lp(0., 0., 1., afP, afD, gfP, rfP, rfD, Lp, L, lbdD, lbdP))
 
-def get_the_transfer_resistance_to_soma(soma, stick, params, precision=100):
+def get_the_transfer_resistance_to_soma(soma, stick, params, precision=100, with_area=False, freq=0.):
+
+    shtn_input = {'fi_prox':0, 'fe_prox':0,'fi_prox':0,
+                  'fe_dist':0,'fi_dist':0}
+    params_for_cable_theory(stick, params)
+    setup_model(soma, stick, params)
+    
+    # model parameters
+    Ls, Ds, l, D, lp, Rm, Cm,\
+        El, Ee, Ei, rm, cm, ri = ball_and_stick_params(soma, stick, params)
+    # activity dependent parameters
+    tauS, tauP, lbdP, tauD, lbdD = \
+            ball_and_stick_constants(shtn_input, soma, stick, params)
+    # cable constants
+    afP, gfP, rfP, afD, rfD, Lp, L = cable_eq_params(freq, tauS, tauP, lbdP,\
+                                    tauD, lbdD, Cm, cm, ri, lp, l, stick['B'])
+                                    
+    Source_Array = np.linspace(0, stick['L'], precision+1)
+    Source_Array = .5*(Source_Array[1:]+Source_Array[:-1]) # discarding the soma, treated below
+    DX = Source_Array[1]-Source_Array[0]
[…]

### 2016-09-19 coupling_model/study_prox_dist_ratio.py
slowly making porgress in the review

@@ -6,6 +6,14 @@ from theory.analytical_calculus import *
 soma, stick, params = np.load('../input_impedance_calibration/mean_model.npy')
 ALL_CELLS = np.load('../input_impedance_calibration/all_cell_params.npy')
 
+
+############# CHANGING THE RATIO ##################
+new_ratio = 12.5 # in percent !
+factor_for_prox_act = 4.
+############# CHANGING THE RATIO ##################
+
+
+
 def find_inh_cond_for_balance(feG, fiG, feI, fiI, fe0, i_nrn, balance, precision=1e2):
     for i in range(len(feG)):
         fiG[i], fiI[i] = find_balance_at_soma(feG[i], feI[i], fe0,\
@@ -16,6 +24,9 @@ def find_inh_cond_for_balance(feG, fiG, feI, fiI, fe0, i_nrn, balance, precision
 def get_fluct_var(i_nrn, F=None, exp_type='non specific activity',\
                   balance=-55e-3, len_f=5, precision=1e2):
 
+    ### CHANGING THE RATIO HERE !! ####
+    ALL_CELLS[i_nrn]['params']['fraction_for_L_prox'] = new_ratio/100.
+    
     if F is None:
         F = np.linspace(0., .4, len_f)
         
@@ -28,22 +39,11 @@ def get_fluct_var(i_nrn, F=None, exp_type='non specific activity',\
     fe0 = find_baseline_excitation(params, soma, stick,\
                                    balance=balance, synch=synch)
     
-    if exp_type=='non specific activity':
-        feG, fiG, feI, fiI = 1.1*F+F0, inh_factor*(0*F+F0), 1.1*F+F0, inh_factor*(0*F+F0)
-        fiG, fiI = find_inh_cond_for_balance(feG, fiG, feI, fiI, fe0,i_nrn, balance+0*F, precision=precision)
-    elif exp_type=='unbalanced activity':
-        feG, feI, fiG, fiI = (F+F0), (F+F0), 0*F, 0*F
-        fiG, fiI = find_inh_cond_for_balance(feG, fiG, feI, fiI, fe0,i_nrn,\
-                                             balance+3e-3*np.linspace(0,1,len(F)), precision=precision)
-    elif exp_type=='proximal activity':
[…]

### 2016-09-20 coupling_model/study_prox_dist_ratio.py
adding other path

@@ -74,6 +74,7 @@ if __name__=='__main__':
 
     import matplotlib.pylab as plt
     sys.path.append('/Users/yzerlaut/work/common_libraries/')
+    sys.path.append('/home/safaai/yann/common_libraries/')
     from graphs.my_graph import set_plot
 
     i_nrn = 2 # index of the neuron

### 2016-09-20 coupling_model/study_prox_dist_ratio.py
version for server

@@ -73,23 +73,17 @@ LABELS2 = ['$\\nu_e^{prox}$(Hz)', '$\\nu_i^{prox}$(Hz)',\
 if __name__=='__main__':
 
     import matplotlib.pylab as plt
-    sys.path.append('/Users/yzerlaut/work/common_libraries/')
     sys.path.append('/home/safaai/yann/common_libraries/')
     from graphs.my_graph import set_plot
 
     i_nrn = 2 # index of the neuron
     precision = 1e4
     
-    fig, AX = plt.subplots(4, 1, figsize=(3.5, 9))
-    plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
-    fig2, AX2 = plt.subplots(5, 1, figsize=(3.5, 10))
-    plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
-    COLORS=['b', 'g']
-
     PROTOCOLS = ['proximal activity', 'distal activity']
                  
     len_f = 30
     F = np.linspace(0, 1, len_f)
+    
     if sys.argv[-2]=='all':
 
         FEG, FIG, FEI, FII, SYNCH, MUV, SV, TVN, MUGN, FOUT =\
@@ -107,6 +101,12 @@ if __name__=='__main__':
             
     elif sys.argv[-1]=='plot':
                 
+        fig, AX = plt.subplots(4, 1, figsize=(3.5, 9))
+        plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
+        fig2, AX2 = plt.subplots(5, 1, figsize=(3.5, 10))
+        plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
+        COLORS=['b', 'g']
+
         FEG, FIG, FEI, FII, SYNCH, MUV, SV, TVN, MUGN, FOUT, new_ratio = np.load('data/synaptic_data_modif.npy')
         fig.suptitle('$f_{prox}$ = '+str(new_ratio)+'%')
             
@@ -122,6 +122,11 @@ if __name__=='__main__':
                     ax.fill_between(F, x.mean(axis=0)-x.std(axis=0),\
                                 x.mean(axis=0)+x.std(axis=0), alpha=.2, color=COLORS[i])
     else:
+        fig, AX = plt.subplots(4, 1, figsize=(3.5, 9))
[…]

### 2016-09-20 coupling_model/study_prox_dist_ratio.py
adding other path

@@ -84,7 +84,7 @@ if __name__=='__main__':
     len_f = 30
     F = np.linspace(0, 1, len_f)
     
-    if sys.argv[-2]=='all':
+    if sys.argv[-1]=='all':
 
         FEG, FIG, FEI, FII, SYNCH, MUV, SV, TVN, MUGN, FOUT =\
            [np.zeros((len(PROTOCOLS), len(ALL_CELLS), len(F))) for j in range(10)]

### 2016-09-20 coupling_model/study_prox_dist_ratio.py
prepared for prox stim

@@ -9,7 +9,7 @@ ALL_CELLS = np.load('../input_impedance_calibration/all_cell_params.npy')
 
 ############# CHANGING THE RATIO ##################
 new_ratio = 12.5 # in percent !
-factor_for_prox_act = 4.
+factor_for_prox_act = 12.
 ############# CHANGING THE RATIO ##################
 
 
@@ -72,9 +72,7 @@ LABELS2 = ['$\\nu_e^{prox}$(Hz)', '$\\nu_i^{prox}$(Hz)',\
 
 if __name__=='__main__':
 
-    import matplotlib.pylab as plt
-    sys.path.append('/home/safaai/yann/common_libraries/')
-    from graphs.my_graph import set_plot
+    sys.path.append('/Users/yzerlaut/work/common_libraries/')
 
     i_nrn = 2 # index of the neuron
     precision = 1e4
@@ -101,6 +99,8 @@ if __name__=='__main__':
             
     elif sys.argv[-1]=='plot':
                 
+        import matplotlib.pylab as plt
+        from graphs.my_graph import set_plot
         fig, AX = plt.subplots(4, 1, figsize=(3.5, 9))
         plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
         fig2, AX2 = plt.subplots(5, 1, figsize=(3.5, 10))
@@ -122,6 +122,8 @@ if __name__=='__main__':
                     ax.fill_between(F, x.mean(axis=0)-x.std(axis=0),\
                                 x.mean(axis=0)+x.std(axis=0), alpha=.2, color=COLORS[i])
     else:
+        import matplotlib.pylab as plt
+        from graphs.my_graph import set_plot
         fig, AX = plt.subplots(4, 1, figsize=(3.5, 9))
         plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
         fig2, AX2 = plt.subplots(5, 1, figsize=(3.5, 10))

### 2016-09-20 review/response_to_reviewer.txt
up review

#+TITLE:  "Heterogeneous Firing Responses Predict Diverse Couplings to Presynaptic Activity in mice Layer V Pyramidal Neurons" \\ _\textsc{ Response to reviewers}_
#+AUTHOR: Y. Zerlaut & A. Destexhe

* Active mechanisms in dendrites

* Reviewer #1

Unfortunately, it is very difficult to grasp the essence and even more
the details of the study.

1) Main statement; presentation. It starts with the title that claims
   that claims that “Heterogeneous Firing Responses Predict Diverse
   Couplings to Presynaptic Activity in mice Layer V Pyramidal
   Neurons”. The title refers to the phenomenology in Figure 5 showing
   that the output frequency goes up or down for different cells as a
   function of “increasing presynaptic quantity”, as the x-axis in
   that figure is label. But not clear how strong the increase is at
   the corresponding position, nor what of the presynaptic quantity
   is. For us (the writer and two other group members) it was neither
   possible to figure it out from the caption nor the text.

   \bf We agree that this way to represent data might not be
   straightforward. We improved the legend of Figure 4 to facilitate
   the comprehension. In particular, we have added an example to
   explicit the presence of "comodulations" of variables and hence the
   difficulty to represent the data as a function of one given
   variable. We believe that this way to present data is still the
   best one to emulate the comodulations that characterize neocortical
   dynamics (e.g. inhibition follows excitation) and to be able to
   represent the response to various forms of network activity
   (i.e. various comodulations) on individual cells.  The new legend
   reads:

   _The abscissa “increasing synaptic quantity” corresponds to the comodulations of the model variables shown in Figure 4A (same color code). As an example, the response to a “proximal activity increase” (blue curve) corresponds to a linear increase of and while keeping , and to their baseline level. See Figure 4A for the comodulations of the other types of increasing activity._
   \rm

2) Main statement unclear. Unfortunately, it does not become clear
   what one has to understand of the “Diverse Couplings to the
   Presynaptic Activity” as expressed in the title. In the abstract it
   is stated: “We indeed found such a heterogeneous response, but
   trivially, the only significant contribution to the various firing
   response was the different levels of cellular excitability.” We
   guess that the “trivially” refers to the fact that only the
   cellular excitability has been modulated in the model. But then we
   don’t understand “A notable exception appeared for proximal
   activity: increasing proximal activity could either promote firing
   response in some cells or suppress it in some other cells whatever
   their individual excitability.” We conclude that there is still
   more than the individual excitability that determines the firing
   behavior, but this seems to contradict the previous statement.

   \bf We agree with the reviewer that the formulation "only [...] except
   [...]" might be misleading, we adapted the abstract to remove this
   source of confusion. Now it reads: "but trivially, the _main_
   significant contribution to the various firing response was the
   different levels of cellular excitability [...]". \rm

#+NAME: fig:1
#+CAPTION: *Changing the ratio of the proximal/distal separation.* *(A)* Configuration of the main text, the proximal part occupies the first 87.5% of the dendritic morphology. *(B)* Now the proximal part occupies only the first 12.5% of the dendritic morphology. This importantly reduces the number of available synapses (the morphology has only one branch in the first 12.5% part). Provided this loss of synapses is compensated by an increase of activity, there is _no qualitative change between the 12.5% and the 87.5% setting for the proximal activity: non-monotonic \(\sigma_V\) variations, strong decrease in \(\tau_V / \tau_m^0 \)_. On the other hand, this change would have important qualitative consequences for the "distal activity" regime, if the last 87.5% of the morphology are "distal", many synapses are electrotonically close (what is rather irrealistic for distal synapses), they will thus stronly interact through conductance shunting and thus produce fluctuations close to the "proximal activity" setting of the main text.
[[./figs/varying_prox_dist.png]]

3) Main statement; missing analysis. It is suggested that the
   heterogeneity would arise from sodium channels, but the paper is
   missing a joint presentation of experimental and modeling data
   showing some fit. Neither could we find a mathematical argument why
   the different phenomenological behavior shown in the cited Fig. 5
   should arise. It would be helpful to underscore the main statement
   by a simplified mathematical formulation in the main text. For
   instance, a simplified formula that gives the output firing rate as
   a function of the input variables would be helpful, including the
   dependencies on the sodium channel density. This sodium channel
   density is claimed to make the difference between the cell types
   according to the abstract: “various levels of density of sodium
   channels and sodium inactivation will control the response of
   individual neurons to proximally targeting presynaptic activity.”
   Again, we could not find a state-of-the-art explanation why this
   statement is true.

   \bf This point is precisely the focus of our previous communication
   [[cite:Zerlaut2016]]. Unfortunately there is, to the best of our knowledge, no
   closed-form solution that could give the firing rate response as a
   response to fluctuating input in a model including sodium
   inactivation and a sdium activation curve (hence the
   phenomenological approach formulated in ou previous
   communication). Nonetheless to give some intuition to the reader,
   we have added the following statement (line 316):
   _In our previous communication, theoretical modeling suggested that a high sensitivity to the speed of the fluctuations was enable by a high level of sodium inactivation (as only fast fluctuations allow to deinactivate sodium channels) and a high density of sodium channels (as it  produces a sharp spike initiation that enables to extract fast fluctuating input)._
   For further details, we believe the reader should refer to our
   previous publication. \rm

4) No dendritic nonlinearities. One main characteristics of L5
   pyramidal neurons is the calcium spike in the apical tree, and more
   generally the various types of dendritic spikes. Non of them is
   considered in the model, and one conjectures that the various
   response properties in the experimental data arise from these
   various dendritic nonlinearities. Describing the firing properties
   of pyramidal neurons as a function of proximal and distal activity
   should take account of these dendritic nonlinearities. Otherwise,
   in fact, the statements cannot be compelling.

   \bf See Part A \rm

5) Data extraction. It is not clear how the 4 cells have been selected
   out of the 27 cells. The 4 cells represent 4 cell types. How are
   these cell types specified? The paper does not give an answer on
   that.

   \bf The 4 cells represent 4 different cells recorded in our
   previous study. (We chose the same 4 cells, as they ). \rm

6) Figure 2 has two panels A & B, but the caption describes panels
   A–E.
   \bf We apologize for this \rm

7) Apart from that, the fit of the numerical simulations and the
   analytical estimate in B for sigma_V is biased. No argument is
   given why this bias is there.

8) The central claim is that distal and proximal inputs differently
   affects the output firing rates. Beside the fact that this
   statement by itself is trivial [...]

   \bf We also show that "distal and proximal inputs differently
   affects the output firing rates", but this is not our main
   statement and we agree with the reviewer that this could seen as
   "trivial". Our main statement claims that those stimulations affect
   individual neurons in diverse manners (in particular for the
   proximal stimulation: increasing their response for some neurons,
   decreasing it for some other neurons). We believe that this
   diversity of responses across neurons (to the same input) is not a
   so trivial phenomena.\rm

9) [...] we wondered why the closer 87.5% of the dendritic branch is
   declared as “proximal” and the furthest 12.5% as the “distal”
   part. Is the result dependent on this choice, or could one have
   also chosen the closer 12.5% as “proximal” only?

   \bf Indeed, the _arbitrary ratio_ between proximal and distal input
   might need a more detailed discussion. Following the reviewer's
   suggestion, we reproduced the analysis with the convention
   "proximal as the closest 12.5% only". We show on [[fig:1][Figure 1]] that the
   results are not affected by this change, the qualitative properties
   of the fluctuations remain identical: strong decrease of the
   fluctuations time constant and non-monotonic shape of the standard
   deviation of the fluctuations. The key property leading to the
   properties of the "proximal activity" being that they correspond to
   synapses that are close to each others and to the soma (to produce
   a strong /shunting/ effect), this phenomena is even stronger under
   this setting. The reason for choosing a relatively large fraction
   for proximal synapses is to obtain a large number of
   synapses. Indeed, along the morphology, the electrotonic distance
   raises but the surface as well (because of the branches number, see
   drawing in Fig 1 in main text) so that the number of synapses
   strongly increases. Summing up, the parameter \(f_{prox}\)=87.5% is
   important to keep the distal part far enough electrotonically, for
   the proximal part there is no much difference between
   \(f_{prox}\)=87.5% and \(f_{prox}\)=12.5% (they all contain the
   very proximal synapses), and keeping \(f_{prox}\)=87.5% avoid to
   introduce an additional rescaling of synaptic frequences because of
   the reduced number of synapses (the procedure shown in [[fig:1][Figure 1]]).

* Reviewer #2

 This manuscript shows a nice mixture of experiment and theory. The
 latter is based upon sensible use of the cable modelling framework of
 Rall combined with stochastic models of synaptic input (admittedly of
 a particular type but definitely fit for purpose).

\bf we thank the reviewer for his \rm

1) Unfortunately some of the work (for the firing response function)
   is buried in supplementary material - and this has not been made
   available to me (S1).

   \bf Sorry to hear this. For us, the link at the end of the
   submission pdf (page 32/32) was functional and actually gave the
   supplementary material. \rm

2) It would be especially informative to hear more about the author's
   perspective on how synchrony controls rate. Nonetheless given the
   quality and novelty of the main manuscript I suggest to put this
   issue aside.

   \bf \rm

** Major concern

My only major concern with the paper is on the emphasis of a
theoretical framework without citing other relevant work in the
area. Essentially I am surprised not to see the mention of the
technique(s) for constructing the Green's function of an arbitrary
branched passive dendritic tree. The paper focuses on Rall equivalent
cylinders for simplicity, yet the methodology presented would seem
easily extended using the work of Abbott [[cite:Abbott1991,Cao1993]]. The
extension of the above to include a distinguished soma model can be
found in [[citetext:Coombes2007]] and Paul Bressloff has done a lot of
work on dendrites that appears relevant, some of which is summarised
in [[citetext:Bressloff1997]]. The following may also be of interest
(though not necessarily for this work) - where simple active soma
models are coupled to passive dendrites
[[cite:Bressloff1995,Svensson2009,Schwemmer2012]].

\bfseries

Indeed, our

We thank the reviewer

\textnormal

** Minor points

Spurious "s" in the sec "A simplified morphological model" - sWe arbitrarily ...
Where is excitability < V_thre^eff >_D defined?

\bf We apologize for the problems with the manuscript preparations and we thank the reviewer for pointing out those mistakes. \rm

* Reviewer #3

The key claim of this work is that recently identified L5 PCs firing
rate properties indicate how these cells couple to presynaptic
activity patterns (proximal, distal,...). The claim is based on i)
recently identified firing response functions (previous work of the
authors), ii) a theoretical model for passive dendritic integration
that is an extension of the single compartment model of
[[citetext:Kuhn2004]] to a passive tree with cable theory, and iii) an
identification of the passive tree of L5 PCs by fitting the input
impedance at the soma to experimental data.

The topic is of importance and the theoretical part is novel, very
appealing in itself and rigorous, but inadequate to support the key
claim of the paper (see paper title).

This is because ...

** CONS

 - *A*: (part ii) For L5 PCs it is highly questionable if dendritic
   integration can be understood without (or separated from) active
   dendritic properties given the known experimental facts and huge
   literature, e.g. about the compartmentalization of dendritic
   function, dendritic spikes, and changed response properties due to
   ion channel blockers.

   In my opinion, the model for the L5 PCs based on a passive tree
   will almost surely fail to describe the real dendritic integration
   properties of the cells in the fluctuation driven regime. In any
   case, see the first point in additional work below.

- *B*: (part iii) Even the description of the passive dendritic
  integration properties of the cell seems to be questionable (maybe
  because of the constraints to symmetrical trees). That this doesn't
  work out properly seems to be reflected in the morphologies obtained
  in the paper: Is the required variation of the tree length from
  about 400 um to 900 um (current Fig 3C and Fig. S1) for PCs
  plausible? Please provide references. L5 PCs with their long apical
  dendrites etc. are the worst case scenario for the symmetry
  constraints for the tree.

** PROS

The theoretical work is still significant for other cell types that
work in a more linear regime, e.g. L2/3 PCs, and have morphologies
that match the theoretical constraints..

** Additional work required:

- The authors should provide evidence that active dendritic
  integration doesn't change the key claim, or, apply the model to a
  more appropriate cell type.

- Because the morphology of the tree of the model is very constraint
  and only a very rough estimate its necessary to assess the influence
  of this approximation on dendritic integration: A systematic
  analysis of the impact of the morphology of the tree (7 variables)
  on the response properties of interest at the soma is missing (This
  allows also a generalization of the results to other cell types. Now
  only Fig S2 gives a hint about variability).

- There's no reference to any other model than [[citetext:Kuhn2004]], on
  which the approach is based. Relate the model to recent work on the
  effects of passive dendritic tree properties of neuron on firing
  dynamics (e.g.  [[citetext:Saparov2015]] or other model reduction
  techniques (a huge field, e.g. [[citetext:Hedrick2013]]).

The paper is well organized, easy to read, simple to follow and
clearly written. However, there are too many typos and word
repetitions to list them all ("sWe" p.3, "show deviations from the
deviations" p.4, " vary the size of the size" p.4, "does not goes",
p.6, "the firing increase show", p.7 ...) and the Figure numbers were
incorrect (Fig.22b, p.4) or mixed up (Fig. 2 and 3).

Minor:

- Fig. 3: The color code seems to be inconsistent: Panel A shows cells
  with Rm above 600 MOhm, but the bottom panel in Fig 3C shows that
  such cells are not present.

- Fig 3C: The lines in the three top panels could be drawn with the
  color code (color changes within a line) as used in panel A and B.

- Fig 3AB: Please comment on the inconsistency between data and model
  for > 100 Hz. There seems to be a flip in vertical order.

Section: "An analytical approximation ...":

- The claim "the analytical estimate could therefore be seen as an accurate estimate, module a shift in the synchrony (~0.2 increase in synchrony corrects for the ~1 mV shift in sigma)" should verified:
1) Results for synchrony = 0.2 should be shown in the right most column of panels in Fig 2B, and
2) results for synchrony = 0.2 should be shown for the other columns of panels in Fig 2B, where the other parameters are varied.

Section: "Biophysical origin ..."

- The characteristics of the firing response function are not properly introduced. Please add this.

- It can be hardly claimed that Fig. 6A is approximately a log normal distribution.

Methods section:

- Not all variables are properly defined, e.g. Qe, Qi, lp.

- "it constitutes an extension of the approach proposed in Kuhn et al. \[19\]": Please, state what extension.

- "Fitting passive properties": Are the solutions unique or are there many different trees with similar fit performance that result in different couplings to presynaptic activity?

* References
\small

#+BEGIN_LATEX
\begin{filecontents}{biblio.bib}

@article{Hedrick2013,
author = {Hedrick, K R and Cox, S J},
doi = {10.1007/s10827-012-0403-y},
issn = {1573-6873 (Electronic) 0929-5313 (Linking)},
journal = {J Comput Neurosci},
number = {1},
pages = {1--26},
title = {{Structure-preserving model reduction of passive and quasi-active neurons}},
type = {Journal Article},
url = {https://www.ncbi.nlm.nih.gov/pubmed/22714391},
volume = {34},
year = {2013}
}

@article{Saparov2015,
  title={Effects of passive dendritic tree properties on the firing dynamics of a leaky-integrate-and-fire neuron},
  author={Saparov, Abulhair and Schwemmer, Michael A},
  journal={Mathematical biosciences},
  volume={269},
  pages={61--75},
  year={2015},
  publisher={Elsevier}
}

@article{Schwemmer2012,
  title={Bistability in a leaky integrate-and-fire neuron with a passive dendrite},
  author={Schwemmer, Michael A and Lewis, Timothy J},
  journal={SIAM Journal on Applied Dynamical Systems},
  volume={11},
  number={1},
  pages={507--539},
  year={2012},
  publisher={SIAM}
}

@article{Bressloff1995,
  title={Dynamics of a compartmental model integrate-and-fire neuron with somatic potential reset},
  author={Bressloff, Paul C},
  journal={Physica D: Nonlinear Phenomena},
  volume={80},
  number={4},
  pages={399--412},
  year={1995},
  publisher={Elsevier}
}

@article{Svensson2009,
author = {Svensson, C.-M. and Coombes, S},
doi = {10.1142/S0218127409024347},
journal = {International Journal of Bifurcation and Chaos},
pages = {2597--2607},
title = {{Mode Locking in a Spatially Extended Neuron Model: Active Soma and Compartmental Tree}},
type = {Journal Article},
volume = {19},
year = {2009}
}

@article{Bressloff1997,
author = {Bressloff, P. C. and Coombes, S.},
doi = {10.1142/S0217979297001209},
file = {:Users/yzerlaut/Documents/Mendeley Desktop/Bressloff, Coombes - 1997 - Physics of the Extended Neuron.pdf:pdf},
issn = {0217-9792},
journal = {International Journal of Modern Physics B},
mendeley-groups = {Neuroscience},
month = {aug},
number = {20},
pages = {2343--2392},
title = {{Physics of the Extended Neuron}},
url = {http://www.worldscientific.com/doi/abs/10.1142/S0217979297001209},
volume = {11},
year = {1997}
}

@article{Coombes2007,
author = {Coombes, S and Timofeeva, Y and Svensson, C-M and Lord, G J and Josi{\'{c}}, K and Cox, S J and Colbert, C M},
doi = {10.1007/s00422-007-0161-5},
file = {:Users/yzerlaut/Documents/Mendeley Desktop/Coombes et al. - 2007 - Branching dendrites with resonant membrane a sum-over-trips approach.pdf:pdf},
issn = {0340-1200},
journal = {Biological cybernetics},
keywords = {Action Potentials,Action Potentials: physiology,Algorithms,Animals,Cell Membrane,Cell Membrane: physiology,Cell Shape,Cell Shape: physiology,Computer Simulation,Dendrites,Dendrites: physiology,Hippocampus,Hippocampus: physiology,Membrane Potentials,Membrane Potentials: physiology,Models, Neurological,Rats,Synaptic Transmission,Synaptic Transmission: physiology},
mendeley-groups = {Neuroscience},
month = {aug},
number = {2},
pages = {137--49},
pmid = {17534649},
title = {{Branching dendrites with resonant membrane: a "sum-over-trips" approach.}},
url = {http://www.ncbi.nlm.nih.gov/pubmed/17534649},
volume = {97},
year = {2007}
}

@article{Cao1993,
author = {Cao, B J and Abbott, L F},
doi = {10.1016/S0006-3495(93)81370-5},
issn = {0006-3495 (Print) 0006-3495 (Linking)},
journal = {Biophys J},
number = {2},
pages = {303--313},
title = {{A new computational method for cable theory problems}},
type = {Journal Article},
url = {https://www.ncbi.nlm.nih.gov/pubmed/8457662},
volume = {64},
year = {1993}
}

@article{Abbott1991,
author = {Abbott, L F and Farhi, E and Gutmann, S},
issn = {0340-1200 (Print) 0340-1200 (Linking)},
journal = {Biol Cybern},
number = {1},
pages = {49--60},
title = {{The path integral for dendritic trees}},
type = {Journal Article},
url = {https://www.ncbi.nlm.nih.gov/pubmed/1768712},
volume = {66},
year = {1991}
}

@article{Zerlaut2016,
author = {Zerlaut, Y and Telenczuk, B and Deleuze, C and Bal, T and Ouanounou, G and Destexhe, A},
doi = {10.1113/JP272317},
issn = {1469-7793 (Electronic) 0022-3751 (Linking)},
journal = {J Physiol},
number = {13},
pages = {3791--3808},
title = {{Heterogeneous firing rate response of mouse layer V pyramidal neurons in the fluctuation-driven regime}},
type = {Journal Article},
url = {http://www.ncbi.nlm.nih.gov/pubmed/27146816},
volume = {594},
year = {2016}
}

@article{Kuhn2004,
abstract = {During sensory stimulation, visual cortical neurons undergo massive synaptic bombardment. This increases their input conductance, and action potentials mainly result from membrane potential fluctuations. To understand the response properties of neurons operating in this regime, we studied a model neuron with synaptic inputs represented by transient membrane conductance changes. We show that with a simultaneous increase of excitation and inhibition, the firing rate first increases, reaches a maximum, and then decreases at higher input rates. Comodulation of excitation and inhibition, therefore, does not provide a straightforward way of controlling the neuronal firing rate, in contrast to coding mechanisms postulated previously. The synaptically induced conductance increase plays a key role in this effect: it decreases firing rate by shunting membrane potential fluctuations, and increases it by reducing the membrane time constant, allowing for faster membrane potential transients. These findings do not depend on details of the model and, hence, are relevant to cells of other cortical areas as well.},
author = {Kuhn, Alexandre and Aertsen, Ad and Rotter, Stefan},
doi = {10.1523/JNEUROSCI.3349-03.2004},
file = {:Users/yzerlaut/Documents/Mendeley Desktop//Kuhn, Aertsen, Rotter - 2004 - Neuronal integration of synaptic input in the fluctuation-driven regime.pdf:pdf},
issn = {1529-2401},
journal = {The Journal of neuroscience : the official journal of the Society for Neuroscience},
keywords = {Action Potentials,Action Potentials: physiology,Animals,Computer Simulation,Excitatory Postsynaptic Potentials,Excitatory Postsynaptic Potentials: physiology,Humans,Membrane Potentials,Membrane Potentials: physiology,Models,Neural Inhibition,Neural Inhibition: physiology,Neurological,Neurons,Neurons: physiology,Synapses,Synapses: physiology,Synaptic Transmission,Synaptic Transmission: physiology,Visual Cortex,Visual Cortex: physiology},
mendeley-groups = {Neuroscience},
month = {mar},
number = {10},
pages = {2345--56},
pmid = {15014109},
publisher = {Soc Neuroscience},
title = {{Neuronal integration of synaptic input in the fluctuation-driven regime.}},
url = {http://www.ncbi.nlm.nih.gov/pubmed/15014109},
volume = {24},
year = {2004}
}
\end{filecontents}
#+END_LATEX

\bibliography{biblio}

* Options :noexport:
# #+OPTIONS: toc:nil num:1
#+OPTIONS: num:1
#+LaTeX_CLASS_OPTIONS: [8pt, a4paper, colorlinks]
#+LaTeX_HEADER: \hypersetup{allcolors = blue} % to have all the hyperlinks in 1 color
#+LaTeX_HEADER: \usepackage{amssymb,mathenv,array}
#+LaTeX_HEADER: \usepackage{microtype} % Slightly tweak font spacing for aesthetics
#+LaTeX_HEADER: \usepackage{geometry}
#+LaTeX_HEADER: \geometry{a4paper,total={210mm,297mm}, left=25mm, right=25mm, top=20mm, bottom=20mm}
#+LaTeX_HEADER: \usepackage{filecontents}
#+LaTeX_HEADER: \renewcommand{\refname}{\vspace{-.8cm}}
#+LaTeX_HEADER: \usepackage{biology_citations}
#+LaTeX_HEADER: \bibliographystyle{biology_citations}
#+LaTeX_HEADER: \renewcommand{\thesection}{\Alph{section}}

### 2016-09-20 coupling_model/study_prox_dist_ratio.py

@@ -9,9 +9,8 @@ ALL_CELLS = np.load('../input_impedance_calibration/all_cell_params.npy')
 
 ############# CHANGING THE RATIO ##################
 new_ratio = 12.5 # in percent !
-factor_for_prox_act = 12.
+factor_for_prox_act = 70.
 ############# CHANGING THE RATIO ##################
-
 
 
 def find_inh_cond_for_balance(feG, fiG, feI, fiI, fe0, i_nrn, balance, precision=1e2):
@@ -41,6 +40,7 @@ def get_fluct_var(i_nrn, F=None, exp_type='non specific activity',\
     
     if exp_type=='proximal activity':
         feG, fiG, feI, fiI = F0+factor_for_prox_act*0.4*F, factor_for_prox_act*0.4*(F+F0), F0, 0*F
+        print(feG)
         fiG, fiI = find_inh_cond_for_balance(feG, fiG, feI, fiI, fe0,i_nrn, balance+0*F, precision=precision)
     elif exp_type=='distal activity':
         feG, fiG, feI, fiI = F0, 0*F, F0+1.3*F, 1.3*inh_factor*(F+F0)
@@ -100,7 +100,6 @@ if __name__=='__main__':
     elif sys.argv[-1]=='plot':
                 
         import matplotlib.pylab as plt
-        from graphs.my_graph import set_plot
         fig, AX = plt.subplots(4, 1, figsize=(3.5, 9))
         plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
         fig2, AX2 = plt.subplots(5, 1, figsize=(3.5, 10))
@@ -123,7 +122,6 @@ if __name__=='__main__':
                                 x.mean(axis=0)+x.std(axis=0), alpha=.2, color=COLORS[i])
     else:
         import matplotlib.pylab as plt
-        from graphs.my_graph import set_plot
         fig, AX = plt.subplots(4, 1, figsize=(3.5, 9))
         plt.subplots_adjust(left=.45, top=.9, wspace=.2, hspace=.2)
         fig2, AX2 = plt.subplots(5, 1, figsize=(3.5, 10))
@@ -140,6 +138,7 @@ if __name__=='__main__':
         plt.show(block=False);input('Hit Enter To Close');plt.close()
 
     if sys.argv[-1]!='all':
+        from graphs.my_graph import set_plot
[…]

### 2016-09-20 input_impedance_calibration/check_surfaces_and_synapses.py

@@ -11,6 +11,9 @@ from input_impedance_calibration.get_calib import adjust_model_prop
 
 soma, stick, params = np.load('../input_impedance_calibration/mean_model.npy')
 
+Ls, Ds, l, D, lp, Rm, Cm,\
+        El, Ee, Ei, rm, cm, ri = ball_and_stick_params(soma, stick, params)
+
 Rm = get_Rm_range()
 
 Ke, Ki = 0*Rm, 0*Rm

### 2016-09-20 theory/analytical_calculus.py

@@ -129,7 +129,6 @@ def cable_eq_params(f, tauS, tauP, lbdP, tauD, lbdD, Cm, cm, ri, lp, l, B):
     # ball and tree rescaling
     Lp = rescale_x(lp, l, lp, B, lbdP, lbdD)
     L = rescale_x(l, l, lp, B, lbdP, lbdD)
-    
     return afP, gfP, rfP, afD, rfD, Lp, L
 
 

### 2016-09-21 numerical_simulations/minimal_synapses.py
adding minimial synapses examples

@@ -1,0 +1,17 @@
+from neuron import h as nrn
+import numpy as np
+import matplotlib.pylab as plt
+
+
+soma = nrn.Section()
+soma.insert('pas')
+soma.L, soma.diam = 58, 58
+soma.g_pas, soma.e_pas = 5e-5, -70.
+syn = nrn.glutamateLarkum2009(0.5, sec=soma)
+netcon = nrn.NetCon(nrn.nil, syn)
+netcon.weight[0] = 3e-9*1e6
+
+
+
+
+

### 2016-09-21 ball_and_rall_tree/check_accuracy.py
adding the draft for the ampa-nmda synapse

@@ -152,7 +152,7 @@ if __name__=='__main__':
                       'fe_prox':fe_baseline, 'fi_prox':fi_baseline,
                       'fe_dist':fe_baseline, 'fi_dist':fi_baseline}
         for s in range(args.SEED):
-            print 'baseline sim. , seed=', s
+            print('baseline sim. , seed=', s)
             t, V = run_simulation(shtn_input, cables, params,\
                                   recordings='soma',
                                   tstop=args.tstop, dt=args.dt, seed=(ii+args.seed+s*(s+1))**3%10000)
@@ -166,7 +166,7 @@ if __name__=='__main__':
                               'fe_prox':EXP['fe_prox'][i], 'fi_prox':EXP['fi_prox'][i],
                               'fe_dist':EXP['fe_dist'][i], 'fi_dist':EXP['fi_dist'][i]}
                 for s in range(args.SEED):
-                    print 'sim=', i, ', seed=', s
+                    print('sim=', i, ', seed=', s)
                     t, V = run_simulation(shtn_input, cables, params,\
                                           recordings='soma',
                                           tstop=args.tstop, dt=args.dt, seed=(ii+args.seed+s*(s+2))**3%10000)
@@ -189,15 +189,15 @@ if __name__=='__main__':
 
     import os
     if not os.path.isfile(file):
-        print '--------------------> input file DOES NOT EXIST'
-        print '--------------------> taking the last one !'
+        print('--------------------> input file DOES NOT EXIST')
+        print('--------------------> taking the last one !')
         file, i, flist ='', 0, os.listdir("data")
         while (file=='') and (i<1e3):
             f = flist[i]
             i+=1
             if len(f.split("vars_"))>1:
                 file = 'data/'+f
-        print file
+        print(file)
   
     # now theoretical plot
     soma, stick, params, SET_OF_EXPS, args = np.load(file)
@@ -207,7 +207,7 @@ if __name__=='__main__':
 
     # plotting all points in all plots so that they have the same boundaries !!
     for EXP in SET_OF_EXPS:
-        for y, i in zip([EXP['muV_exp'], EXP['sV_exp'], EXP['Tv_exp']], range(3)):
[…]

### 2016-09-21 ball_and_rall_tree/demo.py

@@ -70,8 +70,8 @@ def analyze_simulation(xtot, cables, t, V, window_for_autocorrel=50, recordings=
 def get_analytical_estimate(shotnoise_input,
                             soma, stick, params, discret=20):
 
-    print '----------------------------------------------------'
-    print ' Analytical calculus running [...]'
+    print('----------------------------------------------------')
+    print(' Analytical calculus running [...]')
 
     x_th = np.linspace(0, stick['L'], discret)
     
@@ -88,9 +88,9 @@ def get_analytical_estimate(shotnoise_input,
                                   precision=discret)
     # Rin, Rtf = get_the_input_and_transfer_resistance(fe, fi, f, x_th, params, soma, stick)
 
-    print '----------------------------------------------------'
-    print ' => end calculus'
-    print '----------------------------------------------------'
+    print('----------------------------------------------------')
+    print(' => end calculus')
+    print('----------------------------------------------------')
 
     return x_th, muV_th, sV_th, Tv_th
 
@@ -233,7 +233,7 @@ if __name__=='__main__':
     params['factor_for_distal_synapses_tau'] = 1.
     params['factor_for_distal_synapses_weight'] = 2.
 
-    print ' first we set up the model [...]'
+    print(' first we set up the model [...]')
     x_exp, cables = setup_model(soma, stick, params)    
 
     x_stick = np.linspace(0,args.L_stick*1e-6, args.discret_sim+1) # then :
@@ -248,7 +248,7 @@ if __name__=='__main__':
     
     # then we run the simulation if needed
     if args.simulation:
-        print 'Running simulation [...]'
+        print('Running simulation [...]')
         t, V = run_simulation(shotnoise_input, cables, params, tstop=args.tstop_sim, dt=args.dt, seed=args.seed)
         muV_exp, sV_exp, Tv_exp = analyze_simulation(x_exp, cables, t, V)
         np.save(file, [x_exp, shotnoise_input, muV_exp, sV_exp, Tv_exp, soma, stick, params])
@@ -270,10 +270,10 @@ if __name__=='__main__':
                          x_exp, muV_exp, sV_exp, Tv_exp, shotnoise_input)    
         plt.show()
     except IOError:
-        print '======================================================'
-        print 'no numerical data available !!!  '
-        print 'either you run the simulation with the --simulation option !' 
-        print 'either you provide a datafile through the --file option !' 
-        print '======================================================'
+        print('======================================================')
+        print('no numerical data available !!!  ')
[…]

### 2016-09-21 ball_and_rall_tree/test_on_mean_model.py

@@ -20,7 +20,7 @@ if sys.argv[-1]=='run':
     # constructing the space-dependent shotnoise input for the simulation
 
     ## MAKING THE BASELINE EXPERIMENT
-    print 'Running simulation [...]'
+    print('Running simulation [...]')
     t, V = run_simulation(shtn_input, cables, params, tstop=tstop, dt=0.05)
     np.save('data/data_mean_model_sim.npy', [x_exp, shtn_input, cables, t, V])
     
@@ -28,7 +28,7 @@ elif sys.argv[-1]=='analyze':
     x_exp, shtn_input, cables, t, V = \
       np.load('data/data_mean_model_sim.npy')
     x_exp, cables = setup_model(soma, stick, params)    
-    print 'Analyzing data [...]'
+    print('Analyzing data [...]')
     muV_exp, sV_exp, Tv_exp = analyze_simulation(x_exp, cables, t, V)
 
     np.save('data/analyzed_data_mean_model_sim.npy', [x_exp, muV_exp, sV_exp, Tv_exp, shtn_input, soma, stick, params])

### 2016-09-21 numerical_simulations/minimal_synapses.py

@@ -1,7 +1,7 @@
 from neuron import h as nrn
 import numpy as np
 import matplotlib.pylab as plt
-
+from nrn_simulations import *
 
 soma = nrn.Section()
 soma.insert('pas')

### 2016-09-21 numerical_simulations/nrn_simulations.py

@@ -41,8 +41,8 @@ def set_tree_params(EqCylinder, dend, soma, Params):
         Ke_tot += 2**jj*cable['Ke_per_seg']*cable['NSEG']
         if cable['name']!='soma':
             jj+=1
-    print "Total number of EXCITATORY synapses : ", Ke_tot
-    print "Total number of INHIBITORY synapses : ", Ki_tot
+    print(("Total number of EXCITATORY synapses : ", Ke_tot))
+    print(("Total number of INHIBITORY synapses : ", Ki_tot))
     return xtot, cables
 
 def Constructing_the_ball_and_tree(params, cables,
@@ -149,11 +149,11 @@ def Constructing_the_ball_and_tree(params, cables,
     else:
         spkout = np.zeros(0)
         
-    print "======================================="
-    print " --- checking if the neuron is created "
+    print("=======================================")
+    print(" --- checking if the neuron is created ")
     nrn.topology()
-    print "with the total surface : ", area_tot
-    print "======================================="
+    print(("with the total surface : ", area_tot))
+    print("=======================================")
         
     return exc_synapses, exc_netcons, exc_Ks, exc_spike_trains,\
        inh_synapses, inh_netcons, inh_Ks, inh_spike_trains, area_lists, spkout
@@ -248,10 +248,10 @@ def run_simulation(shotnoise_input, cables, params, tstop=2000.,\
         if recordings is 'full':
             V.append(get_v(cables))
 
-    print "======================================="
+    print("=======================================")
     nrn('forall delete_section()')
-    print " --- checking if the neuron is destroyed"
+    print(" --- checking if the neuron is destroyed")
     nrn.topology()
-    print "======================================="
+    print("=======================================")
     return np.array(t_vec), V
 

### 2016-09-21 numerical_simulations/shotnoise.py

@@ -42,7 +42,7 @@ def queue_presynaptic_events_in_NEURON(ALL):
                 for t in spk_train: # loop over events
                     netcon.event(t)
                     ii+=1
-        print ie, ii
+        print((ie, ii))
         return True
     return init_spike_train
 

### 2016-09-21 numerical_simulations/minimal_synapses.py
starting to write the nmda thing

@@ -3,14 +3,32 @@ import numpy as np
 import matplotlib.pylab as plt
 from nrn_simulations import *
 
-soma = nrn.Section()
-soma.insert('pas')
-soma.L, soma.diam = 58, 58
-soma.g_pas, soma.e_pas = 5e-5, -70.
-syn = nrn.glutamateLarkum2009(0.5, sec=soma)
+nrn('create soma')
+nrn.soma.insert('pas')
+nrn.soma.L, nrn.soma.diam = 58, 58
+nrn.soma.g_pas, nrn.soma.e_pas = 5e-5, -70.
+syn = nrn.my_glutamate(0.5, sec=nrn.soma)
 netcon = nrn.NetCon(nrn.nil, syn)
 netcon.weight[0] = 3e-9*1e6
 
+def init_spike_train(ALL):
+    netcon, spikes = ALL
+    for spk in spikes:
+        netcon.event(spk)
+
+# fih = nrn.FInitializeHandler((init_spike_train, [netcon, [50.,100.,150.]]))
+
+# t_vec = nrn.Vector()
+# t_vec.record(nrn._ref_t)
+# V = []
+# V.append(nrn.Vector())
+# exec('V[0].record(nrn.cable_0_0(0)._ref_v)')
+
+# nrn.finitialize(-70.)
+# while nrn.t<200.:
+#     nrn.fadvance()
+
+# plt.plot(np.array(t_vec), V[0], 'k-')
 
 
 

### 2016-09-21 numerical_simulations/nrn_simulations.py

@@ -46,7 +46,7 @@ def set_tree_params(EqCylinder, dend, soma, Params):
     return xtot, cables
 
 def Constructing_the_ball_and_tree(params, cables,
-                                spiking_mech=False):
+                                   spiking_mech=False, nmda_spikes=False):
 
     # list of excitatory stuff
     exc_synapses, exc_netcons, exc_spike_trains, exc_Ks  = [], [], [], []
@@ -104,8 +104,12 @@ def Constructing_the_ball_and_tree(params, cables,
                         Fq = 1.
 
                     # in each segment, we insert an excitatory synapse
-                    syn = nrn.ExpSyn(seg.x, sec=section)
-                    syn.tau, syn.e = Ftau*params['Te']*1e3, params['Ee']*1e3
+                    if nmda_spikes:
+                        syn = my_glutamate(seg.x, sec=section)
+                        syn.tau_ampa, syn.e = Ftau*params['Te']*1e3, params['Ee']*1e3
+                    else:
+                        syn = nrn.ExpSyn(seg.x, sec=section)
+                        syn.tau, syn.e = Ftau*params['Te']*1e3, params['Ee']*1e3
                     exc_synapse.append(syn)
                     netcon = nrn.NetCon(nrn.nil, syn)
                     netcon.weight[0] = Fq*params['Qe']*1e6
@@ -227,11 +231,6 @@ def run_simulation(shotnoise_input, cables, params, tstop=2000.,\
     t_vec.record(nrn._ref_t)
     V = []
 
-    # if recordings is 'soma':
-    #     for rec in recordings:
-    #         V.append(nrn.Vector())
-    #         exec('V[-1].record(nrn.cable_'+str(rec[0])+'_'+str(rec[1])+'('+str(rec[0])+')._ref_v[0]')
-    
     if recordings is 'soma':
         V.append(nrn.Vector())
         exec('V[0].record(nrn.cable_0_0(0)._ref_v)')

### 2016-09-22 active_ball_and_rall_tree/demo.py
adding nmda

@@ -9,7 +9,6 @@ from signanalysis import autocorrel
 sys.path.append('../')
 from theory import brt_drawing
 from theory.analytical_calculus import *
-from numerical_simulations.nrn_simulations import *
 from scipy.optimize import curve_fit
 
 # we calculate the parameters to plug into cable theory
@@ -37,10 +36,9 @@ stick = {'L': 2000*1e-6, 'D': 4*1e-6, 'NSEG': 30,\
          'Ke':100, 'Ki':100., 'name':'dend'}
 
 
-def analyze_simulation(xtot, cables, t, V, window_for_autocorrel=50, recordings='full'):
+def analyze_simulation(xtot, cables, t, V, window_for_autocorrel=50, recordings=1):
 
-
-    if recordings=='full':
+    if recordings==0: # means full recording
         muV_exp, sV_exp, Tv_exp = [], [], []
         
         for i in range(len(cables)): # loop over levels
@@ -58,41 +56,19 @@ def analyze_simulation(xtot, cables, t, V, window_for_autocorrel=50, recordings=
                     Tv_exp[-1] += np.trapz(v_acf, t_shift)/n_level
         muV_exp, sV_exp, Tv_exp = np.array(muV_exp), np.array(sV_exp), np.array(Tv_exp)
         
-    elif recordings=='soma':
+    elif recordings==1: # means soma recording
+        v = np.array(V[0])
+        # discarding transient rise with [len(v)/5:]
+        v_acf, t_shift = autocorrel(v[len(v)/5:], window_for_autocorrel, (t[1]-t[0]))
+        muV_exp, sV_exp, Tv_exp = v[len(v)/5:].mean(), v[len(v)/5:].std(), np.trapz(v_acf, t_shift)
+
+    elif recordings==2: # means soma recording
         v = np.array(V[0])
         # discarding transient rise with [len(v)/5:]
         v_acf, t_shift = autocorrel(v[len(v)/5:], window_for_autocorrel, (t[1]-t[0]))
         muV_exp, sV_exp, Tv_exp = v[len(v)/5:].mean(), v[len(v)/5:].std(), np.trapz(v_acf, t_shift)
         
     return muV_exp, sV_exp, Tv_exp
-
-
-def get_analytical_estimate(shotnoise_input,
-                            soma, stick, params, discret=20):
-
-    print '----------------------------------------------------'
-    print ' Analytical calculus running [...]'
-
[…]

### 2016-09-22 numerical_simulations/minimal_synapses.py

@@ -3,33 +3,38 @@ import numpy as np
 import matplotlib.pylab as plt
 from nrn_simulations import *
 
-nrn('create soma')
-nrn.soma.insert('pas')
-nrn.soma.L, nrn.soma.diam = 58, 58
-nrn.soma.g_pas, nrn.soma.e_pas = 5e-5, -70.
-syn = nrn.my_glutamate(0.5, sec=nrn.soma)
-netcon = nrn.NetCon(nrn.nil, syn)
-netcon.weight[0] = 3e-9*1e6
 
-def init_spike_train(ALL):
-    netcon, spikes = ALL
-    for spk in spikes:
-        netcon.event(spk)
+for ntar, color, label in zip([1, 0], ['b', 'r'], ['NMDA', 'no-NMDA']):
 
-# fih = nrn.FInitializeHandler((init_spike_train, [netcon, [50.,100.,150.]]))
+    nrn('create soma')
+    nrn.soma.insert('pas')
+    nrn.soma.L, nrn.soma.diam = 58, 58
+    nrn.soma.g_pas, nrn.soma.e_pas = 5e-5, -70.
+    syn = nrn.my_glutamate(0.5, sec=nrn.soma)
+    netcon = nrn.NetCon(nrn.nil, syn)
+    netcon.weight[0] = 1
+    syn.gmax = 4
+    def init_spike_train(ALL):
+        netcon, spikes = ALL
+        for spk in spikes:
+            netcon.event(spk)
+    syn.nmda_on = ntar
+    fih = nrn.FInitializeHandler((init_spike_train, [netcon, np.arange(10)*7.+50.]))
+    t_vec = nrn.Vector()
+    t_vec.record(nrn._ref_t)
+    V = nrn.Vector()
+    V.record(nrn.soma(0.5)._ref_v)
+    A = nrn.Vector()
+    A.record(syn._ref_gampa)
 
-# t_vec = nrn.Vector()
-# t_vec.record(nrn._ref_t)
-# V = []
-# V.append(nrn.Vector())
-# exec('V[0].record(nrn.cable_0_0(0)._ref_v)')
+    nrn.finitialize(-70.)
+    while nrn.t<400.:
+        nrn.fadvance()
 
-# nrn.finitialize(-70.)
-# while nrn.t<200.:
-#     nrn.fadvance()
-
-# plt.plot(np.array(t_vec), V[0], 'k-')
-
[…]

### 2016-09-22 numerical_simulations/nrn_simulations.py

@@ -46,7 +46,7 @@ def set_tree_params(EqCylinder, dend, soma, Params):
     return xtot, cables
 
 def Constructing_the_ball_and_tree(params, cables,
-                                   spiking_mech=False, nmda_spikes=False):
+                                   spiking_mech=False, nmda_on=False):
 
     # list of excitatory stuff
     exc_synapses, exc_netcons, exc_spike_trains, exc_Ks  = [], [], [], []
@@ -104,9 +104,10 @@ def Constructing_the_ball_and_tree(params, cables,
                         Fq = 1.
 
                     # in each segment, we insert an excitatory synapse
-                    if nmda_spikes:
-                        syn = my_glutamate(seg.x, sec=section)
+                    if nmda_on:
+                        syn = nrn.my_glutamate(seg.x, sec=section)
                         syn.tau_ampa, syn.e = Ftau*params['Te']*1e3, params['Ee']*1e3
+                        syn.gmax = 1e9*params['Qe'] # nS in my_glutamate.mod
                     else:
                         syn = nrn.ExpSyn(seg.x, sec=section)
                         syn.tau, syn.e = Ftau*params['Te']*1e3, params['Ee']*1e3
@@ -208,13 +209,13 @@ def set_presynaptic_spikes_manually(shotnoise_input, cables, params,\
                                       tstop=tstop, seed=seed+i*j**2, synchrony=synchrony)
 
 def run_simulation(shotnoise_input, cables, params, tstop=2000.,\
-                   dt=0.025, seed=3, recordings='full'):
+                   dt=0.025, seed=3, recordings='full', recordings2='', nmda_on=False):
     """
     recordings is a set of tuple of the form : [branch_generation, branch_number, xseg]
     """
     exc_synapses, exc_netcons, exc_Ks, exc_spike_trains,\
        inh_synapses, inh_netcons, inh_Ks, inh_spike_trains,\
-       area_lists, spkout = Constructing_the_ball_and_tree(params, cables)
+       area_lists, spkout = Constructing_the_ball_and_tree(params, cables, nmda_on=nmda_on)
 
     # then synapses manually
     set_presynaptic_spikes_manually(shotnoise_input, cables, params,\
@@ -234,6 +235,9 @@ def run_simulation(shotnoise_input, cables, params, tstop=2000.,\
     if recordings is 'soma':
         V.append(nrn.Vector())
[…]

### 2016-09-22 active_ball_and_rall_tree/demo.py
adding examples

@@ -71,66 +71,29 @@ def analyze_simulation(xtot, cables, t, V, window_for_autocorrel=50, recordings=
     return muV_exp, sV_exp, Tv_exp
 
 
-def plot_time_traces(t, V, cables, EqCylinder, title='', recordings=[[0,0,0.5]]):
-
-    # time window
-    i1, i2 = 0, min([int(1000/(t[1]-t[0])),len(t)])
-
-    # we define the points that we want to extract
-
-    # ---- soma
-    i_level0, i_branch0, frac_seg0 = 1, 0, 0.
-    i_seg0 = int(frac_seg0*cables[i_level0]['NSEG'])
-    v0 = np.array([V[i][i_level0][i_branch0][i_seg0] for i in range(i1,i2)])
-
-    # ---- medial
-    if len(cables)==2:
-        i_level1, i_branch1 =0, 0
-    else:
-        i_level1, i_branch1= len(cables)/2+1, max([1,2**(len(cables)/2)-1])
-    frac_seg1 =.5
-    i_seg1 = int(frac_seg1*cables[i_level1]['NSEG'])
-    v1 = np.array([V[i][i_level1][i_branch1][i_seg1] for i in range(i1,i2)])
-
-    # ---- distal
-    i_level2, i_branch2, frac_seg2 = len(cables)-1, 0, 1.
-    i_seg2 = int(frac_seg2*cables[i_level2]['NSEG'])-1
-    v2 = np.array([V[i][i_level2][i_branch2][i_seg2] for i in range(i1,i2)])
-    
-    ## first we draw the fig where we will see the inputs
-    fig, ax = brt_drawing.make_fig(EqCylinder, cables[1]['D'],\
-        added_points=[\
-                      [i_level2, i_branch2+1, frac_seg2,'r','D', 10],\
-                      [i_level1, i_branch1+1, frac_seg1,'g','D', 10],\
-                      [i_level0, i_branch0+1, frac_seg0,'b','D', 10]])
-    fig2 = plt.figure()
-
-    plt.title(title)
-    plt.plot(1e-3*t[i1:i2], v0, 'b', label='soma')
-    plt.plot(1e-3*t[i1:i2], v1, 'g', label='medial')
-    plt.plot(1e-3*t[i1:i2], v2, 'r', label='distal')
-    
-    plt.xlabel('time (s)')
-    plt.ylabel('$V_m$ (mV)')
-    plt.legend(loc='best', prop={'size':'small'})
-    plt.tight_layout()
[…]

### 2016-09-22 active_ball_and_rall_tree/run_examples.sh

@@ -1,0 +1,8 @@
+# baseline
+pyth2 demo.py -f data/baseline.npz --mean_model --tstop 2601
+python demo.py -f data/baseline.npz -u
+plot_to_svg data/baseline.npz baseline.svg
+# baseline + stim
+pyth2 demo.py -f data/stim_baseline.npz --mean_model --tstop 2601 --with_synch_stim --DT_syn_stim 500.
+python demo.py -f data/stim_baseline.npz -u
+plot_to_svg data/stim_baseline.npz stim_baseline.svg

### 2016-09-22 numerical_simulations/nrn_simulations.py

@@ -46,7 +46,7 @@ def set_tree_params(EqCylinder, dend, soma, Params):
     return xtot, cables
 
 def Constructing_the_ball_and_tree(params, cables,
-                                   spiking_mech=False, nmda_on=False):
+                                   spiking_mech=False, nmda_on=False, Ca_spikes_on=False, HH_on=False):
 
     # list of excitatory stuff
     exc_synapses, exc_netcons, exc_spike_trains, exc_Ks  = [], [], [], []
@@ -83,6 +83,26 @@ def Constructing_the_ball_and_tree(params, cables,
                 section.insert('pas')
                 section.g_pas = params['g_pas']*1e-4
                 section.e_pas = params['El']*1e3
+                if comp==0 and HH_on:
+	            section.insert('hh3Larkum2009')
+                if (comp==1 or comp==2) and Ca_spikes_on:
+                    section.insert('scaLarkum2009')
+                    section.gbar_scaLarkum2009=10
+	            # section.insert('kdrLarkum2009')
+                    # section.insert('kcaLarkum2009')
+                    # section.gbar_kcaLarkum2009=30
+                    section.insert('cad2Larkum2009')
+	            section.insert('it2Larkum2009')
+                    # section.gcabar_it2Larkum2009=0.000
+	            # section.insert('hh3Larkum2009')
+                    # section.gkbar_hh3Larkum2009=0
+                    # section.gkbar2_hh3Larkum2009=0.0001
+                    # section.gnabar_hh3Larkum2009=0.01
+	            # section.insert('kapLarkum2009')
+                    # section.gkabar_kapLarkum2009=0.003
+	            # section.insert('kmLarkum2009')
+                    # section.gbar_kmLarkum2009=0
+                    # section.gbar_kdrLarkum2009=0
 
                 if level>=1: # if not soma
                     # in NEURON : connect daughter, mother branch
@@ -187,7 +207,8 @@ def get_v(cables):
 
 def set_presynaptic_spikes_manually(shotnoise_input, cables, params,\
                                     exc_spike_trains, exc_Ks,
-                                    inh_spike_trains, inh_Ks, tstop, seed=2):
+                                    inh_spike_trains, inh_Ks, tstop, seed=2,\
+                                    synchronous_stim={'location':[4,14], 'spikes':[]}):
 
     synchrony = shotnoise_input['synchrony']
     
[…]

### 2016-09-22 active_ball_and_rall_tree/check_accuracy.py
working multiple test with nmda and Ca2+ spikes

@@ -1,0 +1,200 @@
+import numpy as np
+import matplotlib.pylab as plt
+import sys, time
+
+
+N_POINTS = 3
+inh_factor = 5.8
+
+fe_baseline, fi_baseline, synch_baseline = 0.2, 0.2*inh_factor, 0.05
+fe_vector = np.array([0.,fe_baseline,0.4])
+fi_vector = np.round(fe_vector*inh_factor,1)
+synch_vector = np.array([0., synch_baseline, 0.4])
+
+def create_set_of_exps(args):
+    SET_OF_EXPS = [\
+                   {'label':'$\\nu_e^p$ (Hz) \n prox. exc. ',
+                    'xticks':fe_vector,
+                    'fe_prox':fe_vector,
+                    'fe_dist':np.ones(N_POINTS)*fe_baseline,
+                    'fi_prox':np.ones(N_POINTS)*fi_baseline,
+                    'fi_dist':np.ones(N_POINTS)*fi_baseline,
+                    'synchrony':np.ones(N_POINTS)*synch_baseline,
+                    'muV_exp_ctrl':np.zeros((N_POINTS, args.SEED)), 'sV_exp_ctrl':np.zeros((N_POINTS, args.SEED)), 'Tv_exp_ctrl':np.zeros((N_POINTS, args.SEED)),
+                    'muV_exp_nmda':np.zeros((N_POINTS, args.SEED)), 'sV_exp_nmda':np.zeros((N_POINTS, args.SEED)), 'Tv_exp_nmda':np.zeros((N_POINTS, args.SEED)),
+                    'Fout_hh':np.zeros((N_POINTS, args.SEED)), 'Fout_all':np.zeros((N_POINTS, args.SEED))
+                    },
+                   {'label':'$\\nu_i^p$ (Hz) \n prox. inh. ',
+                    'xticks':fi_vector,
+                    'fe_prox':np.ones(N_POINTS)*fe_baseline,
+                    'fe_dist':np.ones(N_POINTS)*fe_baseline,
+                    'fi_prox':fi_vector,
+                    'fi_dist':np.ones(N_POINTS)*fi_baseline,
+                    'synchrony':np.ones(N_POINTS)*synch_baseline,
+                    'muV_exp_ctrl':np.zeros((N_POINTS, args.SEED)), 'sV_exp_ctrl':np.zeros((N_POINTS, args.SEED)), 'Tv_exp_ctrl':np.zeros((N_POINTS, args.SEED)),
[…]

### 2016-09-22 active_ball_and_rall_tree/demo.py

@@ -10,6 +10,8 @@ sys.path.append('../')
 from theory import brt_drawing
 from theory.analytical_calculus import *
 from scipy.optimize import curve_fit
+from numerical_simulations.nrn_simulations import *
+nrn.nrn_load_dll('../numerical_simulations/x86_64/.libs/libnrnmech.so')
 
 # we calculate the parameters to plug into cable theory
 
@@ -36,40 +38,38 @@ stick = {'L': 2000*1e-6, 'D': 4*1e-6, 'NSEG': 30,\
          'Ke':100, 'Ki':100., 'name':'dend'}
 
 
-def analyze_simulation(xtot, cables, t, V, window_for_autocorrel=50, recordings=1):
+def analyze_simulation(t, V, Vnmda, Vhh, Vall):
+    i0 = min([len(t)-2,int(100/(t[1]-t[0]))]) # discarding 100ms
+    # subthreshold
+    muV_soma, sV_soma, Tv_soma = [], [], []
+    muV_dend, sV_dend, Tv_dend = [], [], []
+    for v in [V, Vnmda, Vhh, Vall]:
+        muV_soma.append(np.array(v[0])[i0:].mean())
+        sV_soma.append(np.array(v[0])[i0:].std())
+        v_acf, t_shift = autocorrel(np.array(v[0])[i0:], 50, (t[1]-t[0]))
+        Tv_soma.append(np.trapz(v_acf, t_shift))
+        muV_dend.append(np.array(v[1])[i0:].mean())
+        sV_dend.append(np.array(v[1])[i0:].std())
+        v_acf, t_shift = autocorrel(np.array(v[1])[i0:], 50, (t[1]-t[0]))
+        Tv_dend.append(np.trapz(v_acf, t_shift))
+    # spikes
+    vhh, vall = np.array(Vhh[0]), np.array(Vall[0])
+    Fhh = len(t[(vhh[1:]>10) & (vhh[:-1]<10)])/t[-1]
+    Fall = len(t[(vall[1:]>10) & (vall[:-1]<10)])/t[-1]
+    # return muV_soma, sV_soma, Tv_soma, muV_dend, sV_dend, Tv_dend, Fhh, Fall
+    return muV_soma, sV_soma, Tv_soma, Fhh, Fall
 
-    if recordings==0: # means full recording
-        muV_exp, sV_exp, Tv_exp = [], [], []
-        
-        for i in range(len(cables)): # loop over levels
-            n_level = max(1,2**(i-1)) # number of levels
[…]

### 2016-09-22 active_ball_and_rall_tree/run_examples.sh

@@ -1,8 +1,26 @@
-# baseline
+source ~/.bash_profile
+# === baseline ===
 pyth2 demo.py -f data/baseline.npz --mean_model --tstop 2601
 python demo.py -f data/baseline.npz -u
 plot_to_svg data/baseline.npz baseline.svg
-# baseline + stim
-pyth2 demo.py -f data/stim_baseline.npz --mean_model --tstop 2601 --with_synch_stim --DT_syn_stim 500.
+# === baseline + stim ===
+pyth2 demo.py -f data/stim_baseline.npz --mean_model --tstop 2601 --with_synch_stim --DT_synch_stim 500.
 python demo.py -f data/stim_baseline.npz -u
 plot_to_svg data/stim_baseline.npz stim_baseline.svg
+# === proximal stim ===
+pyth2 demo.py -f data/prox.npz --mean_model --tstop 2601 --fe_prox 1.1 --fi_prox 9.
+python demo.py -f data/prox.npz -u
+plot_to_svg data/prox.npz prox.svg
+# === distal stim ===
+pyth2 demo.py -f data/dist.npz --mean_model --tstop 2601 --fe_dist 0.6 --fi_dist 3.
+python demo.py -f data/dist.npz -u
+plot_to_svg data/dist.npz dist.svg
+# === synchrony stim ===
+pyth2 demo.py -f data/synch.npz --mean_model --tstop 2601 --synchrony 0.55
+python demo.py -f data/synch.npz -u
+plot_to_svg data/synch.npz synch.svg
+# === unbalanced stim ===
+pyth2 demo.py -f data/unbalanced.npz --mean_model --tstop 2601 --fe_dist 0.4 --fi_dist 1.5 --fe_prox 0.3 --fi_prox 1.
+python demo.py -f data/unbalanced.npz -u
+plot_to_svg data/unbalanced.npz unbalanced.svg
+

### 2016-09-23 active_ball_and_rall_tree/check_accuracy.py
done prelimanry fig

@@ -92,7 +92,7 @@ for EXP in SET_OF_EXPS:
             ax.plot(-0.+0*y, 1.1*y, 'wD', lw=0, alpha=0.)
             ax.plot(-0.+0*y, .9*y, 'wD', lw=0, alpha=0.)
 YTICKS = [[-70,-60,-50], [3,5,7], [12, 20, 28], [0,10,20]]
-YLIM = [[-75,-40], [1.9,8.], [9,31], [-2,30]]
+YLIM = [[-75,-30], [1.9,10.], [9,45], [-2,30]]
 for EXP, ii in zip(SET_OF_EXPS, list(range(len(SET_OF_EXPS)))):
     for ax, y1, x, yticks, ylim, col in zip(AX[:,ii],\
                                       [EXP['muV_exp_ctrl'], EXP['sV_exp_ctrl'], EXP['Tv_exp_ctrl'], EXP['Fout_hh']],\
@@ -148,6 +148,7 @@ if __name__=='__main__':
         np.savez(args.filename, **data)
     else:
         from demo import *
+        nrn.nrn_load_dll('../numerical_simulations/x86_64/.libs/libnrnmech.so')
         soma, stick, params = np.load('../input_impedance_calibration/mean_model.npy')
         stick['NSEG'] = args.discret_sim
     

### 2016-09-23 review/response_to_reviewer.txt
short txt update

@@
 * Active mechanisms in dendrites
+
+Common to two reviewers, so we adressed it in details
+
+We included dendritic non-linearities as provided by the model of
+[[citetext:Larkum2009]] ([[https://senselab.med.yale.edu/modeldb/showModel.cshtml?model=124043][found on ModelDB]]), see [[fig:0a][Figure 1]], and studied
+their impact in the fluctuation-driven regime, see [[fig:0b][Figure 2]].
+
+#+NAME: fig:0a
+#+CAPTION: *Including dendritic non-linearities within our framework for single cell computation (numerical study).* *(A)* Response Baseline activity.
+[[./figs/traces.pdf]]
+
+#+NAME: fig:0b
+#+CAPTION: *Effect of dendritic non-linearities in the subthreshold fluctuations and firing response in the fluctuation-dirven regime.* *(A)* 
+[[./figs/active_sum_up.pdf]]
 
@@
    suggestion, we reproduced the analysis with the convention
-   "proximal as the closest 12.5% only". We show on [[fig:1][Figure 1]] that the
+   "proximal as the closest 12.5% only". We show on [[fig:1][Figure 3]] that the
    results are not affected by this change, the qualitative properties
@@
    introduce an additional rescaling of synaptic frequences because of
-   the reduced number of synapses (the procedure shown in [[fig:1][Figure 1]]).
+   the reduced number of synapses (the procedure shown in [[fig:1][Figure 3]]).
 
@@
 \begin{filecontents}{biblio.bib}
+
+@article{Larkum2009,
+author = {Larkum, M E and Nevian, T and Sandler, M and Polsky, A and Schiller, J},
+doi = {10.1126/science.1171958},
+issn = {1095-9203 (Electronic) 0036-8075 (Linking)},
+journal = {Science},
+number = {5941},
+pages = {756--760},
+title = {{Synaptic integration in tuft dendrites of layer 5 pyramidal neurons: a new unifying principle}},
+type = {Journal Article},
+url = {http://www.ncbi.nlm.nih.gov/pubmed/19661433 http://science.sciencemag.org/content/sci/325/5941/756.full.pdf},
+volume = {325},
+year = {2009}
+}
 

### 2016-09-23 active_ball_and_rall_tree/demo.py
factor 1e3 for output frequency

@@ -54,7 +54,10 @@ def analyze_simulation(t, V, Vnmda, Vhh, Vall):
         Tv_dend.append(np.trapz(v_acf, t_shift))
     # spikes
     vhh, vall = np.array(Vhh[0]), np.array(Vall[0])
+    print(t[(vhh[1:]>10) & (vhh[:-1]<10)])
+    print(len(t[(vhh[1:]>10) & (vhh[:-1]<10)]))
     Fhh = len(t[(vhh[1:]>10) & (vhh[:-1]<10)])/t[-1]
+    print(1e3*Fhh)
     Fall = len(t[(vall[1:]>10) & (vall[:-1]<10)])/t[-1]
     # return muV_soma, sV_soma, Tv_soma, muV_dend, sV_dend, Tv_dend, Fhh, Fall
     return muV_soma, sV_soma, Tv_soma, Fhh, Fall
@@ -83,8 +86,8 @@ AX[0].plot(data['t'], data['Vnmda'][1], 'r-', label='NMDA')
 AX[0].legend(prop={'size':'xx-small'})
 AX[1].plot(data['t'], data['V'][0], 'k-', label='Control (passive + AMPA + GABA)')
 AX[1].plot(data['t'], data['Vnmda'][0], 'r-', label='Control + NMDA')
-AX[1].plot(data['t'], data['Vhh'][0], 'b-', label='Control + HH (soma)')
-AX[1].plot(data['t'], data['Vall'][0], 'g--', alpha=.3, lw=3, label='Control + NMDA + HH (soma) + Ca spikes')
+AX[1].plot(data['t'], 1e3*data['Vhh'][0], 'b-', label='Control + HH (soma)')
+AX[1].plot(data['t'], 1e3*data['Vall'][0], 'g--', alpha=.3, lw=3, label='Control + NMDA + HH (soma) + Ca spikes')
 AX[1].legend(prop={'size':'xx-small'})
 if args.with_synch_stim:
     tt=args.DT_synch_stim

### 2016-09-23 active_ball_and_rall_tree/check_accuracy.py
final fig done

@@ -91,12 +91,12 @@ for EXP in SET_OF_EXPS:
         for ax in AX[i,:]:
             ax.plot(-0.+0*y, 1.1*y, 'wD', lw=0, alpha=0.)
             ax.plot(-0.+0*y, .9*y, 'wD', lw=0, alpha=0.)
-YTICKS = [[-70,-60,-50], [3,5,7], [12, 20, 28], [0,10,20]]
-YLIM = [[-75,-30], [1.9,10.], [9,45], [-2,30]]
+YTICKS = [[-70,-60,-50], [3,5,7], [12, 20, 28], [0,15,30]]
+YLIM = [[-75,-30], [1.9,10.], [9,45], [-2,40]]
 for EXP, ii in zip(SET_OF_EXPS, list(range(len(SET_OF_EXPS)))):
     for ax, y1, x, yticks, ylim, col in zip(AX[:,ii],\
-                                      [EXP['muV_exp_ctrl'], EXP['sV_exp_ctrl'], EXP['Tv_exp_ctrl'], EXP['Fout_hh']],\
-                                      [EXP['muV_exp_nmda'], EXP['sV_exp_nmda'], EXP['Tv_exp_nmda'], EXP['Fout_all']],\
+                                      [EXP['muV_exp_ctrl'], EXP['sV_exp_ctrl'], EXP['Tv_exp_ctrl'], 1e3*EXP['Fout_hh']],\
+                                      [EXP['muV_exp_nmda'], EXP['sV_exp_nmda'], EXP['Tv_exp_nmda'], 1e3*EXP['Fout_all']],\
                                       YTICKS, YLIM, ['r','r','r','g']):
         ax.errorbar(np.linspace(-.2,.2,len(y1)), np.array(y1).mean(axis=1),\
                     yerr=np.array(y1).std(axis=1), marker='D', color='k')

### 2016-09-23 review/response_to_reviewer.txt
adding figures

@@
 
-* Active mechanisms in dendrites
+* Impact of active dendritic mechanisms
 
-Common to two reviewers, so we adressed it in details
+\bfseries
 
-We included dendritic non-linearities as provided by the model of
-[[citetext:Larkum2009]] ([[https://senselab.med.yale.edu/modeldb/showModel.cshtml?model=124043][found on ModelDB]]), see [[fig:0a][Figure 1]], and studied
-their impact in the fluctuation-driven regime, see [[fig:0b][Figure 2]].
+Two reviewers raised the concern that active dendritic mechanisms
+could qualitatively affect the claim of our study. We address their
+concern in the following.
+
+How could active dendritic mechanisms "qualitatively affect the claim
+of our study" ? Our framework for single cell computation consists in
+(i) evaluating analytically the somatic subthreshold membrane
+potential fluctuations at the soma as a function of the presynaptic
+quantities and (ii) convert those fluctuations into a spiking
+probability thanks to a /firing response/ function determined /in
+vitro/ in individual neuron thanks to somatic recordings.
+
+Our framework thus needs to be tested against two phenomena: (I)
+whether active dendritic mechanisms qualitatively affect the
+relationship between presynaptic quantities and somatic membrane
+potential fluctuations and (II) whether dendritic non-linearities
+introduce a coupling between presynaptic activity and spike emission
+that render the decomposition into the successive steps i & ii
+misleading. Those phenomena will naturally appear to some extent and
+will produce quantitative deviations with respect to our predictions
+(that neglects dendritic non-linearities), the purpose of this study
+is only to check for "qualitative deviations".
+
+To investigate the impact of those phenomena, we included active
+dendritic mechanisms (as provided by the model of [[citetext:Larkum2009]],
+available on ModelDB, [[https://senselab.med.yale.edu/modeldb/showModel.cshtml?model=124043][link]]) into our framework for cellular
+computation in the /fluctuation-driven/ regime. We included two of the
+principal ingredients of active dendritic mechanisms into our model:
+(i) NMDA currents (coupled to the AMPA synapses) and (ii) Ca^{2+}
+spikes. We performed a numerical study on the /mean/ morphological
+model of the main text (Table 1 and Figure 2,3), we spread those
+mechanisms according to the picture provided by the study of
+[[citetext:Larkum2009]], all glutamatergic synapses were replaced by the
+AMPA+NMDA synapses and Ca^{2+} currents were included in the last two
+branches to provide a /relay/ for far dendritic events (depicted in
+the mean model drawing of [[fig:0a][Figure 1]]). Phenomenon (I) will be tested
+against the inclusion of the NMDA mechanism and phenomenon (II) will
+be tested against the inclusion of both NMDA and Ca^{2+} spikes.
 
@@
 [[./figs/traces.pdf]]
+
+In [[fig:0a][Figure 1]], we represent the output of the numerical simulations of
+the resulting model. We show on [[fig:0a][Figure 1]]A,C-F the response to the five
+protocols discussed within the manuscript. Additionally, on [[fig:0a][Figure 1]]B,
+we added another type stimulus
+
+[[cite:Stuart2015]]
+
+show the their impact in the
+fluctuation-driven regime, see [[fig:0b][Figure 2]].
+
+\normalfont
 
@@
 
+@article{Stuart2015,
+author = {Stuart, Greg J and Spruston, Nelson},
+doi = {10.1038/nn.4157},
+file = {:Users/yzerlaut/Documents/Mendeley Desktop/Stuart, Spruston - 2015 - Dendritic integration 60 years of progress.pdf:pdf},
+issn = {1097-6256},
+journal = {Nature Neuroscience},
+mendeley-groups = {Neuroscience},
+number = {12},
+pages = {1713--1721},
+pmid = {26605882},
+title = {{Dendritic integration: 60 years of progress}},
+url = {http://www.nature.com/doifinder/10.1038/nn.4157},
+volume = {18},
+year = {2015}
+}
+
 @article{Larkum2009,

### 2016-09-23 review/response_to_reviewer.txt
update review

@@
 * Impact of active dendritic mechanisms
-
-\bfseries
 
@@
 against the inclusion of the NMDA mechanism and phenomenon (II) will
-be tested against the inclusion of both NMDA and Ca^{2+} spikes.
+be tested against the inclusion of both NMDA and Ca^{2+} spikes. Those
+two situations will be compared to the picture described in the main text.
 
 #+NAME: fig:0a
-#+CAPTION: *Including dendritic non-linearities within our framework for single cell computation (numerical study).* *(A)* Response Baseline activity.
+#+CAPTION: *Including dendritic non-linearities (numerically) within our framework for single cell computation.
+On top of each panel, we present the recording of the membrane potential in the far distal dendrite (depicted with the upper electrode on the drawing) in the Control and Control+NMDA case.
+On the bottom, we present the membrane potential recorded at the soma (depicted with the lower electrode on the drawing) in four cases, the Control, the Control+NMDA case, the Control case with a HH model inserted in the soma and the Control+NMDA+Ca^{2+}spikes+HH(soma)*.
+*(A)* Response to baseline activity.
+\(\nu_e^p=\nu_e^d\)=0.2Hz, \(\nu_i^p=\nu_i^d\)=1.2Hz and s=0.05.
+*(B)* Response to baseline activity with the synchronous activation of 20 synapses every 500ms (marked by a triangle), note the impact of the NMDA mechanism under this stimulation type.
+*(C)* Response to an increase of proximal activity with respect to the baseline level (\(\nu_e^p\)=1.6Hz, \(\nu_i^p\)=10Hz).
+*(D)* Response to an increase in distally targetting presynaptic activity.
+*(E)* Response to an increase in unbalanced activity.
+*(F)* Response to an increase in
 [[./figs/traces.pdf]]
@@
 
-\normalfont
-
 #+NAME: fig:0b
@@
 
-Unfortunately, it is very difficult to grasp the essence and even more
-the details of the study.
+\it Unfortunately, it is very difficult to grasp the essence and even more
+the details of the study. \rm
 
-1) Main statement; presentation. It starts with the title that claims
+1) \it Main statement; presentation. It starts with the title that claims
    that claims that “Heterogeneous Firing Responses Predict Diverse
@@
    is. For us (the writer and two other group members) it was neither
-   possible to figure it out from the caption nor the text.
+   possible to figure it out from the caption nor the text. \rm
 
-   \bf We agree that this way to represent data might not be
+    We agree that this way to represent data might not be
    straightforward. We improved the legend of Figure 4 to facilitate
@@
 See Figure 4A for the comodulations of the other types of increasing activity._
-   \rm
 
-2) Main statement unclear. Unfortunately, it does not become clear
+2) \it Main statement unclear. Unfortunately, it does not become clear
    what one has to understand of the “Diverse Couplings to the
@@
    more than the individual excitability that determines the firing
-   behavior, but this seems to contradict the previous statement.
+   behavior, but this seems to contradict the previous statement. \rm
 
-   \bf We agree with the reviewer that the formulation "only [...] except
+   We agree with the reviewer that the formulation "only [...] except
    [...]" might be misleading, we adapted the abstract to remove this
@@
    significant contribution to the various firing response was the
-   different levels of cellular excitability [...]". \rm
+   different levels of cellular excitability [...]".
 
@@
 
-3) Main statement; missing analysis. It is suggested that the
+3) \it Main statement; missing analysis. It is suggested that the
    heterogeneity would arise from sodium channels, but the paper is
@@
    Again, we could not find a state-of-the-art explanation why this
-   statement is true.
+   statement is true. \rm
 
-   \bf This point is precisely the focus of our previous communication
+    This point is precisely the focus of our previous communication
    [[cite:Zerlaut2016]]. Unfortunately there is, to the best of our knowledge, no
@@
    For further details, we believe the reader should refer to our
-   previous publication. \rm
+   previous publication.
 
-4) No dendritic nonlinearities. One main characteristics of L5
+4) \it No dendritic nonlinearities. One main characteristics of L5
    pyramidal neurons is the calcium spike in the apical tree, and more
@@
    should take account of these dendritic nonlinearities. Otherwise,
-   in fact, the statements cannot be compelling.
+   in fact, the statements cannot be compelling. \rm
 
-   \bf See Part A \rm
+   We adressed this concern in details in Part A.
 
-5) Data extraction. It is not clear how the 4 cells have been selected
+5) \it Data extraction. It is not clear how the 4 cells have been selected
    out of the 27 cells. The 4 cells represent 4 cell types. How are
    these cell types specified? The paper does not give an answer on
-   that.
+   that. \rm
 
-   \bf The 4 cells represent 4 different cells recorded in our
-   previous study. (We chose the same 4 cells, as they ). \rm
+   The 4 cells represent 4 different cells out of the n=30 cells
+   recorded in our previous study [[cite:Zerlaut2016]]. The criteria to
+   choose those 4 cells was that they should somehow represent
+   different behaviors while still being representative. See in Figure
+   6B in [[citetext:Zerlaut2016]] how those 4 cells cover relatively well
+   the domain of measured characteristics for the firing response,
+   this is also the case in the present study, where they cover
+   relatively well the domain of the predicted coupling to the various
+   types of activities.
 
-6) Figure 2 has two panels A & B, but the caption describes panels
-   A–E.
-   \bf We apologize for this \rm
+6) \it Figure 2 has two panels A & B, but the caption describes panels
+   A–E. \rm
 
-7) Apart from that, the fit of the numerical simulations and the
+   Indeed, we apologize for this problem in the manuscript
+   preparation. Figure 2 and Figure 3 have been mixed up...
+
+7) \it Apart from that, the fit of the numerical simulations and the
    analytical estimate in B for sigma_V is biased. No argument is
-   given why this bias is there.
+   given why this bias is there. \rm
 
-8) The central claim is that distal and proximal inputs differently
+   From line 165 to line 182, we discuss the validity of our
+   analytical treatment. We explicit the two hypothesis that underlie
+   our estimation and detail their expected effect. We conclude by
+   discussing the bias for \(\sigma)V\) from line 180 to 182: "Some
+   discrepancies between the approximation and the simulations
+   appeared, in particular one can see a 1mV shift in the standard
+   deviation of the fluctuation (meaning that single events are
+   underestimated in the analytical treatment, so that hypothesis 2 is
+   the most problematic one)." (where hypothesis 2 has been explicited
+   before).
+
+8) \it The central claim is that distal and proximal inputs differently
    affects the output firing rates. Beside the fact that this
-   statement by itself is trivial [...]
+   statement by itself is trivial [...] \rm
 
-   \bf We also show that "distal and proximal inputs differently
+   We also show that "distal and proximal inputs differently
    affects the output firing rates", but this is not our main
@@
    diversity of responses across neurons (to the same input) is not a
-   so trivial phenomena.\rm
+   so trivial phenomena.
 
-9) [...] we wondered why the closer 87.5% of the dendritic branch is
+9) \it [...] we wondered why the closer 87.5% of the dendritic branch is
    declared as “proximal” and the furthest 12.5% as the “distal”
    part. Is the result dependent on this choice, or could one have
-   also chosen the closer 12.5% as “proximal” only?
+   also chosen the closer 12.5% as “proximal” only? \rm
 
-   \bf Indeed, the _arbitrary ratio_ between proximal and distal input
+   Indeed, the _arbitrary ratio_ between proximal and distal input
    might need a more detailed discussion. Following the reviewer's
@@
 
-The key claim of this work is that recently identified L5 PCs firing
+\it The key claim of this work is that recently identified L5 PCs firing
 rate properties indicate how these cells couple to presynaptic
@@
 
-This is because ...
+This is because ... \rm
 

### 2016-09-27 review/response_to_reviewer.txt
ädding new final check sim theory

@@
 Two reviewers raised the concern that active dendritic mechanisms
-could qualitatively affect the claim of our study. We address their
-concern in the following.
+(reviewed in [[citetext:Stuart2015]]) could qualitatively affect the claim
+of our study. We address their concern in the following.
 
@@
 of our study" ? Our framework for single cell computation consists in
-(i) evaluating analytically the somatic subthreshold membrane
+(*i*) evaluating analytically the somatic subthreshold membrane
 potential fluctuations at the soma as a function of the presynaptic
-quantities and (ii) convert those fluctuations into a spiking
+quantities and (*ii*) convert those fluctuations into a spiking
 probability thanks to a /firing response/ function determined /in
@@
 
-Our framework thus needs to be tested against two phenomena: (I)
+Our framework thus needs to be tested against two phenomena: (*I*)
 whether active dendritic mechanisms qualitatively affect the
 relationship between presynaptic quantities and somatic membrane
-potential fluctuations and (II) whether dendritic non-linearities
-introduce a coupling between presynaptic activity and spike emission
-that render the decomposition into the successive steps i & ii
-misleading. Those phenomena will naturally appear to some extent and
-will produce quantitative deviations with respect to our predictions
-(that neglects dendritic non-linearities), the purpose of this study
-is only to check for "qualitative deviations".
+potential fluctuations, i.e. checking the validity of step *i*, and
+(*II*) whether dendritic non-linearities introduce a coupling between
+presynaptic activity and spike emission that render the decomposition
+into the successive steps *i* & *ii* misleading. Those phenomena will
+naturally appear to some extent and will produce quantitative
+deviations with respect to our predictions (that do not include
+dendritic non-linearities, e.g. trivially, all cells should be more
+excitable). As the main message of the paper does not rely on the
+absolute values of the input-output functions but on the rather on the
+relative behaviors from cell to cell that emerge from differences
+across individual firing response functions, the purpose of this study
+is only to investigate putative "qualitative deviations".
 
@@
 dendritic mechanisms (as provided by the model of [[citetext:Larkum2009]],
-available on ModelDB, [[https://senselab.med.yale.edu/modeldb/showModel.cshtml?model=124043][link]]) into our framework for cellular
-computation in the /fluctuation-driven/ regime. We included two of the
-principal ingredients of active dendritic mechanisms into our model:
-(i) NMDA currents (coupled to the AMPA synapses) and (ii) Ca^{2+}
-spikes. We performed a numerical study on the /mean/ morphological
-model of the main text (Table 1 and Figure 2,3), we spread those
-mechanisms according to the picture provided by the study of
-[[citetext:Larkum2009]], all glutamatergic synapses were replaced by the
-AMPA+NMDA synapses and Ca^{2+} currents were included in the last two
-branches to provide a /relay/ for far dendritic events (depicted in
-the mean model drawing of [[fig:0a][Figure 1]]). Phenomenon (I) will be tested
-against the inclusion of the NMDA mechanism and phenomenon (II) will
-be tested against the inclusion of both NMDA and Ca^{2+} spikes. Those
-two situations will be compared to the picture described in the main text.
+available on ModelDB on the following [[https://senselab.med.yale.edu/modeldb/showModel.cshtml?model=124043][link]]) into our framework for
+cellular computation in the /fluctuation-driven/ regime. We included
+two of the principal ingredients of non-linear dendritic mechanisms
+into our model: NMDA currents (coupled to the AMPA synapse) and
+Ca^{2+} currents. We performed a numerical study on the /mean/
+morphological model of the main text (Table 1 and Figure 2,3), we
+spread those mechanisms according to the picture provided by the study
+of [[citetext:Larkum2009]], all glutamatergic synapses were replaced by
+the AMPA+NMDA synapses and Ca^{2+} currents were included in the last
+two branches to provide a /relay/ for far dendritic events (depicted
+on the drawing of the mean model, see [[fig:0a][Figure 1]]). Phenomenon (*I*) will
+be tested against the inclusion of the NMDA mechanism, we will examine
+the properties of the membrane potential fluctuations at the soma,
+with and without this mechanism. Phenomenon (*II*) will be tested
+against the inclusion of both NMDA and Ca^{2+} currents: we will first
+include numerically a spike emission model at the soma (Hodgkin-Huxley
+like, Na^{+} and K^{+} currents) in the morphological model, then the
+model will be able to produce the full input-output function (from
+presynaptic quantities to spiking probability), we will then
+investigate how NMDA and Ca^{2+} currents impacts the dependency on
+the presynaptic variables for the full input-output function.
 
@@
 *(C)* Response to an increase of proximal activity with respect to the baseline level (\(\nu_e^p\)=1.6Hz, \(\nu_i^p\)=10Hz).
-*(D)* Response to an increase in distally targetting presynaptic activity.
-*(E)* Response to an increase in unbalanced activity.
-*(F)* Response to an increase in
+*(D)* Response to an increase in distally targetting presynaptic activity (\(\nu_e^d\)=0.6Hz, \(\nu_i^d\)=3Hz).
+*(E)* Response to an increase in unbalanced activity (\(\nu_e^p\)=0.4Hz, \(\nu_i^p\)=2Hz,\(\nu_e^p\)=0.5Hz, \(\nu_i^p\)=1.7Hz).
+*(F)* Response to an increase in presynaptic synchrony (s=0.4).
 [[./figs/traces.pdf]]
-
-In [[fig:0a][Figure 1]], we represent the output of the numerical simulations of
-the resulting model. We show on [[fig:0a][Figure 1]]A,C-F the response to the five
-protocols discussed within the manuscript. Additionally, on [[fig:0a][Figure 1]]B,
-we added another type stimulus
-
-[[cite:Stuart2015]]
-
-show the their impact in the
-fluctuation-driven regime, see [[fig:0b][Figure 2]].
 
@@
 [[./figs/active_sum_up.pdf]]
+
+In [[fig:0a][Figure 1]], we represent the output of the numerical simulations of
+the resulting models. We represent the subthreshold responses on top
+plots, as well as the responses in presence of a spiking mechanism
+(the HH model at the soma) on bottom plots. We show on [[fig:0a][Figure 1]]A,C-F
+the response to the five protocols discussed within the
+manuscript. Additionally, on [[fig:0a][Figure 1]]B, we added another type of
+stimulus: the synchronous activation of 20 synapses on one distal
+dendrite. The response to this last stimulus clearly exhibits the
+presence of strong NMDA currents resembling those observed /in vivo/
+[[cite:Larkum2009]]. We observe that, for the /baseline activity/, for the
+/strong proximal activity/ and for the /strong distal activity/, there
+does not seems to be a strong impact of the NMDA mechanism on the
+subthreshold fluctuations (both at the soma and in the distal
+dendrites): it exerts a slight depolarization but does not
+qualitatively impacts the fluctuations. Neither the triggering of
+action potentials seems to be affected (spikes are identically evoked
+with and without NMDA and Ca^{2+} channels in presence of a somatic HH
+model), see [[fig:0a][Figure 1]]A,C,D. On the other hand, for a high level of
+unbalanced activity (where excitation globally overcomes inhibition),
+we observe a strong depolarization induced by the NMDA mechanism, we
+also observe that, consequently, the spiking probability seems
+significantly increased, see [[fig:0a][Figure 1]]E. Also for a high level of
+synchrony the fluctuations and spikes seems to be affected, we observe
+the presence of small NMDA spikes and additional spikes are elicited
+in the presence of NMDA and Ca^{2+} currents, see [[fig:0a][Figure 1]]E.
+
+We then analyze with more details how those active mechanisms impacts
+the dependency on the variables of the model. We thus reproduced the
+analysis of Figure 3 in the main text. On [[fig:0b][Figure 2]]A, we report the
+properties of the fluctuations as a function of the presynaptic
+variables, with and without NMDA channels. We observe that NMDA
+channels exert an additional small depolarization (increased
+\(\mu_V\)), increase the standard deviation of the fluctuations
+because they increase the amplitude of depolarizing events (increased
+\(\sigma_V\)) and they slow down the fluctuations because they slowly
+increase the low frequency content of post-synaptic depolarization
+(increased \(\tau_V\)). We also observe, that, despite this small
+shift in all quantities, the qualitative trend of all curves remain
+identical. Only for high excitation a qualitative difference can be
+observe (see bottom left plot of [[fig:0b][Figure 2]]A): increasing excitation
+makes V_m fluctuations faster in the passive case whereas increasing
+excitation makes fluctuations slower in the presence of NMDA currents
+(decreasing vs increasing \(\tau_V\) curve respectively). We conclude
+that phenomenon *I* has a very weak impact provided excitation does
+not overcome inhibition and provided that synchrony remains in a
+relatively low range (the range of our study: $s \leq 0.4\)).
+
+On [[fig:0b][Figure 2]]B, we investigate how NMDA and Ca^{2+} currents shape the
+dependency of the spiking probability on the presynaptic
+variables. Trivially, we observe an increased spiking probability
+because cells are more excitable (NMDA and Ca^{2+} currents are
+depolarizing currents). Notably, when excitation does not balance
+inhibition (\(\nu_e^p = 0.4\)Hz or \(\nu_i^p = 0\)Hz), the spiking
+probability is greatly enhanced (almost doubled). For the other
+variables, those effects are much more moderate. Here again, we
+conclude that phenomenon *II* has a weak impact provided excitation
+does not overcome inhibition and provided that synchrony remains in a
+relatively low range (the range of our study: $s \leq 0.4\)).
+
+As can be seen in [[fig:0a][Figure 1]]B, those results nonetheless apply only to
+neocortical processing when effects are mediated by /weakly
+synchronous and relatively balanced/ population dynamics, when single
+cell response is driven by synchronous activation of multiple
+synapses, dendritic nonlinearities have a crucial impact (consistent
+with experimental evidences and the current view on dendritic
+processing, reviewed in [[citetext:Stuart2015]]). We thus modified the
+main text to briefly mention the results of the present analysis and
+our conclusions. The main text now reads:
+
+\bf The proposed theoretical framework for single-cell computation
+nonetheless suffers from several weaknesses. [...]. Most importantly,
+there is no active mechanisms in dendrites [[cite:Hausser2005]], it is
+therefore a question how much those mechanisms could affect the
+picture provided in our study. Preliminary numerical analysis
+performed in presence of NMDA and Ca2+ currents [[cite:Larkum2009]],
+showed that, provided excitation balances inhibition (a situation
+where NMDA channels keeps a relatively low level of stationary
+activation) and provided synchrony do not reach a too high level (so
+that excitatory events have a weak probability to evoke NMDA and
+Ca^{2+} spikes), the qualitative behavior of the cellular input-output
+function remains identical. Our preliminary analysis thus suggest the
+hypothesis that active dendritic mechanisms may not be crucial for
+effects mediated by slow (T\(\geq\)20-30ms) variations of weakly synchronous
+population dynamics while being critical for operations performed on
+synchronous synaptic activations (T\(\leq\)5-10ms), consistent with the
+current view on dendritic processing [[cite:Stuart2015]]. Future work
+should address this hypothesis in details. \rm
+
+Because we believe that those results constitute only preliminary data
+and that this problem should be the focus of a much more detailed
+analysis, we do not wish to include it in the main text or
+supplementary material. If the reviewer think that this is important
+for our study, we can merge [[fig:0a][Figure 1]] and [[fig:0b][Figure 2]] and produce a
+supplementary figure whose legend will be adapted from this section
+and the current legends.
 
@@
 
-   _The abscissa “increasing synaptic quantity” corresponds to the comodulations of the model variables shown in Figure 4A (same color code).
-As an example, the response to a “proximal activity increase” (blue curve) corresponds to a linear increase of and while keeping , and to their baseline level.
-See Figure 4A for the comodulations of the other types of increasing activity._
+   \bf The abscissa “increasing synaptic quantity” corresponds to the
+   comodulations of the model variables shown in Figure 4A (same color
+   code). As an example, the response to a “proximal activity
+   increase” (blue curve) corresponds to a linear increase of
+   \(\nu_e^{prox}\) and \(\nu_i^{prox}\) while keeping
+   \(\nu_e^{dist}\), \(\nu_i^{dist}\) and \(s\) to their baseline
+   level. See Figure 4A for the comodulations of the other types of
+   increasing activity. \rm
 
@@
    [...]" might be misleading, we adapted the abstract to remove this
-   source of confusion. Now it reads: "but trivially, the _main_
+   source of confusion. Now it reads: \bf "but trivially, the _main_
    significant contribution to the various firing response was the
-   different levels of cellular excitability [...]".
+   different levels of cellular excitability [...]". \rm
 
@@
    This point is precisely the focus of our previous communication
-   [[cite:Zerlaut2016]]. Unfortunately there is, to the best of our knowledge, no
-   closed-form solution that could give the firing rate response as a
-   response to fluctuating input in a model including sodium
-   inactivation and a sdium activation curve (hence the
-   phenomenological approach formulated in ou previous
+   [[cite:Zerlaut2016]]. Unfortunately there is, to the best of our
+   knowledge, no closed-form solution that could give the firing rate
+   response as a response to fluctuating input in a model including
+   sodium inactivation and a sodium activation curve (hence the
+   phenomenological approach formulated in our previous
    communication). Nonetheless to give some intuition to the reader,
-   we have added the following statement (line 316):
-   _In our previous communication, theoretical modeling suggested that a high sensitivity to the speed of the fluctuations was enable by a high level of sodium inactivation (as only fast fluctuations allow to deinactivate sodium channels) and a high density of sodium channels (as it  produces a sharp spike initiation that enables to extract fast fluctuating input)._
-   For further details, we believe the reader should refer to our
-   previous publication.
+   we have added the following statement (line 316): \bf In our
+   previous communication, theoretical modeling suggested that a high
+   sensitivity to the speed of the fluctuations was enable by a high
+   level of sodium inactivation (as only fast fluctuations allow to
+   deinactivate sodium channels) and a high density of sodium channels
+   (as it produces a sharp spike initiation that enables to extract
+   fast fluctuating input). \rm For further details, we believe the
+   reader should refer to our previous publication.
 
@@
    relatively well the domain of the predicted coupling to the various
-   types of activities.
+   types of activities, see Figure 6 in main text. We updated the
+   manuscript to highlight this point (line 250): \bf We show on
+   Figure 5 the response of four cells (representative of different
+   firing response behaviors, see Figure 5 and 6B in
+   [[citetext:Zerlaut2016]]) to the different types of presynaptic
+   activity described in the previous section. The input-output
+   relationships show qualitative and quantitative differences, [...]
+   \rm
 
@@
    Indeed, we apologize for this problem in the manuscript
-   preparation. Figure 2 and Figure 3 have been mixed up...
+   preparation. Figure 2 and Figure 3 have been mixed up, this is now
+   corrected.
 
@@
 
- This manuscript shows a nice mixture of experiment and theory. The
- latter is based upon sensible use of the cable modelling framework of
- Rall combined with stochastic models of synaptic input (admittedly of
- a particular type but definitely fit for purpose).
+ \it This manuscript shows a nice mixture of experiment and
+ theory. The latter is based upon sensible use of the cable modelling
+ framework of Rall combined with stochastic models of synaptic input
+ (admittedly of a particular type but definitely fit for purpose). \rm
 
-\bf we thank the reviewer for his \rm
+1) \it Unfortunately some of the work (for the firing response function)
+   is buried in supplementary material - and this has not been made
+   available to me (S1).\rm
 
-1) Unfortunately some of the work (for the firing response function)
-   is buried in supplementary material - and this has not been made
-   available to me (S1).
+   That is indeed unfortunate. For us, the permanent link at the end
+   of the submission pdf (page 32/32) was functional and actually gave
+   the supplementary material. Maybe the reviewer could ask the editor
+   for this material if this is still not available in this
+   resubmission.
 
-   \bf Sorry to hear this. For us, the link at the end of the
-   submission pdf (page 32/32) was functional and actually gave the
-   supplementary material. \rm
-
-2) It would be especially informative to hear more about the author's
+2) \it It would be especially informative to hear more about the author's
    perspective on how synchrony controls rate. Nonetheless given the
    quality and novelty of the main manuscript I suggest to put this
-   issue aside.
+   issue aside. \rm
 
-   \bf \rm
+   This is indeed an interesting point. In the present study, we give
+   a first order description of the effect of synchrony on stationary
+   firing rate (in the /weakly synchronous/ regime, close to an
+   idealized /asynchronous/ regime): presynaptic synchrony between
+   presynaptic events increases the variance of the fluctuations that
+   in turn increases the firing rate. But there should be effect
+   beyond this first order description, when we go further and further
+   from the idealized asynchronous state, i.e. when the firing rate
+   can not be obtained from the stationary fluctuations
+   properties. Interactions between synchrony and dendritic
+   non-linearities also appear important to neocortical cell
+   processing (see Part A of this response). Following the reviewer's
+   opinion, we would also prefer to leave this issue aside as those
+   are quite complicated questions and perform detailed investigations
+   in future work.
 
@@
 
-My only major concern with the paper is on the emphasis of a
+\it My only major concern with the paper is on the emphasis of a
 theoretical framework without citing other relevant work in the
@@
 models are coupled to passive dendrites
-[[cite:Bressloff1995,Svensson2009,Schwemmer2012]].
+[[cite:Bressloff1995,Svensson2009,Schwemmer2012]]. \rm
 
-\bfseries
+We are grateful to the reviewer for those bibliographical
+suggestions. This allowed us to detail the possible extension of our
+framework to more complex dendritic structures. The updated discussion
+now reads (line 335): \bf To investigate those effects within the
+framework proposed in our study, one could benefit from the large body
+of theoretical work on the derivation of Green’s function for
+arbitrary branched passive dendritic trees
+[[cite:Abbott1991,Cao1993,Bressloff1997,Coombes2007]]. \rm
 
-Indeed, our
+Nonetheless, for clarity for the reader (not to be pointed toward more
+complex methods than just Rall's method), we keep only the reference
+to Rall's work in the Methods and Results section. Then the author can
+be more focused on the originality of our approach: the use of
+shotnoise theory results in a dendritic integration context.
 
-We thank the reviewer
+In addition, we have given some perspective about the approach used
+here to obtain the firing rate response in presence of a dendritic
+structure. In the discussion, one can now find the sentence (line
+361):
 
-\textnormal
+\bf This phenomenological two-steps procedure thus offers a flexible
+complementary approach to the analytical approaches tackling the
+problem of the spiking behavior in presence of an extended dendritic
+structure [[cite:Svensson2009,Schwemmer2012,Saparov2015]]. \rm
 
@@
 
-Spurious "s" in the sec "A simplified morphological model" - sWe arbitrarily ...
-Where is excitability < V_thre^eff >_D defined?
+1) \it Spurious "s" in the sec "A simplified morphological model" - sWe arbitrarily ... \rm
 
-\bf We apologize for the problems with the manuscript preparations and we thank the reviewer for pointing out those mistakes. \rm
+Thanks. corrected.
+
+2) \it Where is excitability < V_thre^eff >_D defined? \rm
+
+Thanks. This was indeed only briefly mentionned in a main text as a
+reference to our previous study, now in the Methods section, we added:
+
+\bf Importantly, our study introduced four quantities to describe the
+mean properties of a single neuron response in the fluctuation-driven
+regime: (i) a measure of the excitability given by the mean
+phenomenological threshold \( \langle V_{thre}^eff \rangle_\mathcal{D}
+\) of our firing rate function, (ii) a sensitivity to the mean of the
+fluctuations \( \langle \frac{\partial \nu}{\partial \mu_V}
+\rangle_\mathcal{D} \), i.e. quantifying how much a mean
+depolarization is translated into a change in firing rate, (iii) a
+sensitivity to the amplitude of the fluctuations \( \langle
+\frac{\partial \nu}{\partial \sigma_V} \rangle_\mathcal{D} \),
+quantifying how much an increase of the standard deviation of the
+fluctuations is translated into a change in firing rate, and (iv) a
+sensitivity to the speed of the fluctuations \( \langle \frac{\partial
+\nu}{\partial \tau_V^N} \rangle_\mathcal{D} \), quantifying how much a
+change in the autocorrelation time of the fluctuations is translated
+into a change in firing rate. \rm
 
@@
 
- - *A*: (part ii) For L5 PCs it is highly questionable if dendritic
+ - *A*: \it (part ii) For L5 PCs it is highly questionable if dendritic
    integration can be understood without (or separated from) active
@@
    properties of the cells in the fluctuation driven regime. In any
-   case, see the first point in additional work below.
+   case, see the first point in additional work below. \rm
 
-- *B*: (part iii) Even the description of the passive dendritic
+   We adressed in details the question of dendritic nonlinearities in
+   Part A. The question of the compartementalization of dendritic
+   function is indeed something not adressed in our study, we would
+   prefer to leave this aspect for future investigations.
+
+- *B*: \it (part iii) Even the description of the passive dendritic
   integration properties of the cell seems to be questionable (maybe
@@
   dendrites etc. are the worst case scenario for the symmetry
-  constraints for the tree.
+  constraints for the tree. \rm
+
+  We totally agree with the reviewer on this point. We removed the
+  point stating that our simplified morphology could somehow resemble
+  those of layer V pyramidal cells. More precisely, we removed the
+  following statement: \bf Also the obtained morphology seems
+  realistic (B=5 generation of branches, a total tree length of =550m
+  and a root branch diameter of the tree =2.25m) given what can be
+  observed after histological work [[cite:Zerlaut2016]] \rm. The emphasis
+  should remain on the electrical properties.
+
+  Importantly, the results of our study do not rely on having a
+  precise description of the morphology, we only use this to
+  discriminate between a proximal and a distal area, and Rall's
+  symmetric branching model is sufficient to reproduce this feature.
+  So in the discussion, we aknowledge the important limitations of our
+  morphological model and stress the above point (what is the
+  important ingredient in our study) with:
+
+ \bf [...] even if our description captures the various electrotonic
+  distances associated to various synaptic locations (the crucial
+  ingredient here to discriminate between proximal and distal inputs),
+  the morphological model appears as a _very poor description of layer
+  V pyramidal cell_. Deviations from the symmetric branching
+  hypothesis and Rall's branching rule will have a significant impact
+  on dendritic integration in the fluctuation-driven regime. To
+  investigate those effects [...] \rm
 
@@
 
-The theoretical work is still significant for other cell types that
+\it The theoretical work is still significant for other cell types that
 work in a more linear regime, e.g. L2/3 PCs, and have morphologies
-that match the theoretical constraints..
+that match the theoretical constraints.. \rm
 
@@
 
-- The authors should provide evidence that active dendritic
+- \it The authors should provide evidence that active dendritic
   integration doesn't change the key claim, or, apply the model to a
-  more appropriate cell type.
+  more appropriate cell type. \rm
 
-- Because the morphology of the tree of the model is very constraint
-  and only a very rough estimate its necessary to assess the influence
-  of this approximation on dendritic integration: A systematic
-  analysis of the impact of the morphology of the tree (7 variables)
-  on the response properties of interest at the soma is missing (This
-  allows also a generalization of the results to other cell types. Now
-  only Fig S2 gives a hint about variability).
+  see Part A of this response
 
-- There's no reference to any other model than [[citetext:Kuhn2004]], on
-  which the approach is based. Relate the model to recent work on the
-  effects of passive dendritic tree properties of neuron on firing
+- \it Because the morphology of the tree of the model is very
+  constraint and only a very rough estimate its necessary to assess
+  the influence of this approximation on dendritic integration: A
+  systematic analysis of the impact of the morphology of the tree (7
+  variables) on the response properties of interest at the soma is
+  missing (This allows also a generalization of the results to other
+  cell types. Now only Fig S2 gives a hint about variability). \rm
+
+  *TO BE DONE*
+
+- \it There's no reference to any other model than [[citetext:Kuhn2004]],
+  on which the approach is based. Relate the model to recent work on
+  the effects of passive dendritic tree properties of neuron on firing
   dynamics (e.g.  [[citetext:Saparov2015]] or other model reduction
-  techniques (a huge field, e.g. [[citetext:Hedrick2013]]).
+  techniques (a huge field, e.g. [[citetext:Hedrick2013]]). \rm
 
-The paper is well organized, easy to read, simple to follow and
-clearly written. However, there are too many typos and word
-repetitions to list them all ("sWe" p.3, "show deviations from the
-deviations" p.4, " vary the size of the size" p.4, "does not goes",
-p.6, "the firing increase show", p.7 ...) and the Figure numbers were
-incorrect (Fig.22b, p.4) or mixed up (Fig. 2 and 3).
+  The updated discussion now reads (line 335): \bf To investigate
+  those effects within the framework proposed in our study, one could
+  benefit from the large body of theoretical work on the derivation of
+  Green’s function for arbitrary branched passive dendritic trees
+  [[cite:Abbott1991,Cao1993,Bressloff1997,Coombes2007]]. \rm In addition,
+  we have given some perspective about the approach used here to
+  obtain the firing rate response in presence of a dendritic
+  structure. In the discussion, one can now find the sentence (line
+  361): \bf This phenomenological two-steps procedure thus offers a
+  flexible complementary approach to the analytical approaches
+  tackling the problem of the spiking behavior in presence of an
+  extended dendritic structure
+  [[cite:Svensson2009,Schwemmer2012,Saparov2015]]. \rm
 
-Minor:
+\it The paper is well organized, easy to read, simple to follow and
+clearly written.
 
-- Fig. 3: The color code seems to be inconsistent: Panel A shows cells
+However, there are too many typos and word repetitions to list them
+all ("sWe" p.3, "show deviations from the deviations" p.4, " vary the
+size of the size" p.4, "does not goes", p.6, "the firing increase
+show", p.7 ...) and the Figure numbers were incorrect (Fig.22b, p.4)
+or mixed up (Fig. 2 and 3). \rm
+
+We apologize for the problems in the manuscript preparation (the
+figures mixed up) and we thank the reviewer for pointing out the
+typos... From now on, even if the question refer to the (wrong)
+previous notation ex-Figure 3 will be renamed to Figure 2 as in the
+re-submission.
+
+** Minor:
+
+- \it Fig. 3: The color code seems to be inconsistent: Panel A shows cells
   with Rm above 600 MOhm, but the bottom panel in Fig 3C shows that
-  such cells are not present.
+  such cells are not present. \rm
 
-- Fig 3C: The lines in the three top panels could be drawn with the
-  color code (color changes within a line) as used in panel A and B.
+  This is because those data come from two separate datasets, we
+  highlighted this with the mention of "firing rate dataset" at the
+  bottom of panel 2C. We have a special dataset to investigate the
+  input impedance properties (on the exact same experimental model)
+  where 2 cells were more resistive than those present in the other
+  dataset. We use this dataset to derive a "sizing rule" from the
+  input resistance and then be able to use the "firing rate dataset"
+  where we only have the input resistance (and not the detailed input
+  impedance spectrum). Note that, as expected from the same
+  exerimental system, the datasets were statistically pretty similar:
+  355.9 \(\pm\) 184.1 M\(\Omega\) for the "firing rate dataset", see
+  [[citetext:Zerlaut2016]] and 387.3 \(\pm\) 197.2 M\(\Omega\) for the
+  "input impedance dataset", see Methods.
 
-- Fig 3AB: Please comment on the inconsistency between data and model
-  for > 100 Hz. There seems to be a flip in vertical order.
+  We have updated figure 2C with the mention of "n=30cells" for the
+  "firing rate dataset", then it highlights the difference with the
+  dataset of input impedance labeled "n=13cells" and makes it more
+  clear to the reader.
 
-Section: "An analytical approximation ...":
+- \it Fig 3C: The lines in the three top panels could be drawn with the
+  color code (color changes within a line) as used in panel A and B. \rm
 
-- The claim "the analytical estimate could therefore be seen as an accurate estimate, module a shift in the synchrony (~0.2 increase in synchrony corrects for the ~1 mV shift in sigma)" should verified:
-1) Results for synchrony = 0.2 should be shown in the right most column of panels in Fig 2B, and
-2) results for synchrony = 0.2 should be shown for the other columns of panels in Fig 2B, where the other parameters are varied.
+  Very good idea, thanks ! See new Figure 2.
+
+- \it Fig 3AB: Please comment on the inconsistency between data and model
+  for > 100 Hz. There seems to be a flip in vertical order. \rm
+
+  *TO BE DONE*
+
+\it Section: "An analytical approximation ...":
+
+- The claim "the analytical estimate could therefore be seen as an
+  accurate estimate, modulo a shift in the synchrony (~0.2 increase in
+  synchrony corrects for the ~1 mV shift in sigma)" should
+  verified: 1) Results for synchrony = 0.2 should be shown in the
+  right most column of panels in Fig 2B, and 2) results for synchrony
+  = 0.2 should be shown for the other columns of panels in Fig 2B,
+  where the other parameters are varied. \rm
+
+  *TO BE DONE*
 
@@
 
-- The characteristics of the firing response function are not properly introduced. Please add this.
+- \it The characteristics of the firing response function are not properly
+  introduced. Please add this. \rm
 
-- It can be hardly claimed that Fig. 6A is approximately a log normal distribution.
+  This is indeed a very important point, thanks, we updated the
+  methods section with:
 
-Methods section:
+  \bf Importantly, our study introduced four quantities to describe
+  the mean properties of a single neuron response in the
+  fluctuation-driven regime: (i) a measure of the excitability given
+  by the mean phenomenological threshold \( \langle V_{thre}^eff
+  \rangle_\mathcal{D} \) of our firing rate function, (ii) a
+  sensitivity to the mean of the fluctuations \( \langle
+  \frac{\partial \nu}{\partial \mu_V} \rangle_\mathcal{D} \),
+  i.e. quantifying how much a mean depolarization is translated into a
+  change in firing rate, (iii) a sensitivity to the amplitude of the
+  fluctuations \( \langle \frac{\partial \nu}{\partial \sigma_V}
+  \rangle_\mathcal{D} \), quantifying how much an increase of the
+  standard deviation of the fluctuations is translated into a change
+  in firing rate, and (iv) a sensitivity to the speed of the
+  fluctuations \( \langle \frac{\partial \nu}{\partial \tau_V^N}
+  \rangle_\mathcal{D} \), quantifying how much a change in the
+  autocorrelation time of the fluctuations is translated into a change
+  in firing rate. \rm
 
-- Not all variables are properly defined, e.g. Qe, Qi, lp.
+- \it It can be hardly claimed that Fig. 6A is approximately a log normal
+  distribution. \rm
 
-- "it constitutes an extension of the approach proposed in Kuhn et al. \[19\]": Please, state what extension.
+  We agree. What we actually mean is that the data appears to be
+  distributed logarithmically, we do not wish to put a special
+  emphasis on the log-normal trend. The statement "approximatelly
+  log-normal" was a concise way to express this trend. If this is a
+  problem, we could change it to "the data appears to be distributed
+  logarithmically and not linearly" but we are not sure that this
+  formulation would render better the idea.
 
-- "Fitting passive properties": Are the solutions unique or are there many different trees with similar fit performance that result in different couplings to presynaptic activity?
+\it Methods section: \rm
+
+- \it Not all variables are properly defined, e.g. Qe, Qi, lp. \rm
+
+  Indeed, thanks. We updated the Methods section (mostly the "Model
+  equations" section).
+
+- \it "it constitutes an extension of the approach proposed in Kuhn et
+  al.": Please, state what extension. \rm
+
+  Done, it now reads: \bf it extends the approach proposed in Kuhn et
+  al. to the extended dendritic structure following Rall’s branching
+  rule \rm
+
+- \it "Fitting passive properties": Are the solutions unique or are there
+  many different trees with similar fit performance that result in
+  different couplings to presynaptic activity? \rm
+
+  *TO BE DONE*
 
@@
 \begin{filecontents}{biblio.bib}
+
+@article{Hausser2005,
+author = {London, Michael and H{\"{a}}usser, Michael},
+doi = {10.1146/annurev.neuro.28.061604.135703},
+issn = {0147-006X (Print)$\backslash$r0147-006X (Linking)},
+journal = {Annual review of neuroscience},
+pages = {503--532},
+title = {{Dendritic computation.}},
+type = {Journal Article},
+volume = {28},
+year = {2005}
+}
 

### 2016-09-27 ball_and_rall_tree/final_check_accuracy.py

@@ -1,0 +1,295 @@
+import numpy as np
+import matplotlib.pylab as plt
+import sys, time
+sys.path.append('../code')
+from my_graph import set_plot
+import fourier_for_real as rfft
+sys.path.append('../')
+from theory.analytical_calculus import *
+from data_firing_response.analyze_data import get_Rm_range
+from input_impedance_calibration.get_calib import adjust_model_prop
+from demo import *
+
+from firing_response_description.template_and_fitting import final_func
+
+N_POINTS = 5
+N_POINTS_TH = 10
+inh_factor = 5.8
+
+fe_baseline, fi_baseline, synch_baseline = 0.2, 0.2*inh_factor, 0.05
+fe_vector = np.array([0.,0.1,fe_baseline,0.3,0.4])
+fi_vector = np.round(fe_vector*inh_factor,1)
+fe_vector_th = np.linspace(0., 0.4, N_POINTS_TH)
+fi_vector_th = fe_vector_th*inh_factor
+synch_vector = np.array([0.0, 0.02, synch_baseline, 0.15, 0.4])
+synch_vector_plot = np.array([0.01, 0.02, synch_baseline, 0.15, 0.4])
+synch_vector_th=np.logspace(np.log(0.01)/np.log(10),np.log(0.01)/np.log(10),N_POINTS_TH)
+
+def create_set_of_exps(args):
+    SET_OF_EXPS = [\
+                   {'label':'$\\nu_e^p$ (Hz) \n prox. exc. ',
+                    'xticks':fe_vector,
+                    'fe_prox':fe_vector,
+                    'fe_dist':np.ones(N_POINTS)*fe_baseline,
+                    'fi_prox':np.ones(N_POINTS)*fi_baseline,
+                    'fi_dist':np.ones(N_POINTS)*fi_baseline,
+                    'synchrony':np.ones(N_POINTS)*synch_baseline,
+                    'muV_exp':np.zeros((N_POINTS, args.SEED)), 'sV_exp':np.zeros((N_POINTS, args.SEED)), 'Tv_exp':np.zeros((N_POINTS, args.SEED))
+                    },
+                   {'label':'$\\nu_i^p$ (Hz) \n prox. inh. ',
+                    'xticks':fi_vector,
+                    'fe_prox':np.ones(N_POINTS)*fe_baseline,
+                    'fe_dist':np.ones(N_POINTS)*fe_baseline,
+                    'fi_prox':fi_vector,
+                    'fi_dist':np.ones(N_POINTS)*fi_baseline,
[…]

### 2016-09-27 ball_and_rall_tree/final_check_accuracy.py
done with the graph

@@ -8,9 +8,8 @@ sys.path.append('../')
 from theory.analytical_calculus import *
 from data_firing_response.analyze_data import get_Rm_range
 from input_impedance_calibration.get_calib import adjust_model_prop
-from demo import *
-
 from firing_response_description.template_and_fitting import final_func
+from demo import *
 
 N_POINTS = 5
 N_POINTS_TH = 10
@@ -23,7 +22,9 @@ fe_vector_th = np.linspace(0., 0.4, N_POINTS_TH)
 fi_vector_th = fe_vector_th*inh_factor
 synch_vector = np.array([0.0, 0.02, synch_baseline, 0.15, 0.4])
 synch_vector_plot = np.array([0.01, 0.02, synch_baseline, 0.15, 0.4])
-synch_vector_th=np.logspace(np.log(0.01)/np.log(10),np.log(0.01)/np.log(10),N_POINTS_TH)
+synch_vector_th_plot=np.logspace(np.log(0.01)/np.log(10),np.log(0.4)/np.log(10),N_POINTS_TH)
+synch_vector_th = synch_vector_th_plot
+synch_vector_th[0] = 0
 
 def create_set_of_exps(args):
     SET_OF_EXPS = [\
@@ -65,7 +66,7 @@ def create_set_of_exps(args):
                     },
                    {'label':'synchrony',
                     'xlabel':'synchrony',
-                    'xticks':synch_vector,
+                    'xticks':synch_vector_plot,
                     'fe_prox':np.ones(N_POINTS)*fe_baseline,
                     'fe_dist':np.ones(N_POINTS)*fe_baseline,
                     'fi_prox':np.ones(N_POINTS)*fi_baseline,
@@ -84,7 +85,7 @@ def create_set_of_exps_th(args):
                     'fi_prox':np.ones(N_POINTS_TH)*fi_baseline,
                     'fi_dist':np.ones(N_POINTS_TH)*fi_baseline,
                     'synchrony':np.ones(N_POINTS_TH)*synch_baseline,
-                    'muV_exp':np.zeros((N_POINTS_TH, args.SEED)), 'sV_exp':np.zeros((N_POINTS_TH, args.SEED)), 'Tv_exp':np.zeros((N_POINTS_TH, args.SEED))
+                    'muV':np.zeros(N_POINTS_TH), 'sV':np.zeros(N_POINTS_TH), 'Tv':np.zeros(N_POINTS_TH)
                     },
                    {'label':'$\\nu_i^p$ (Hz) \n prox. inh. ',
[…]

### 2016-09-27 firing_response_description/template_and_fitting.py

@@ -2,7 +2,6 @@ import numpy as np
 from scipy.optimize import minimize
 from scipy.optimize import curve_fit, leastsq
 import scipy.special as sp_spec
-import statsmodels.api as sm
 
 ## NORMALIZING COEFFICIENTS
 # needs to be global here, because used both in the function

### 2016-09-27 input_impedance_calibration/calibrate.sh

@@ -1,8 +1,17 @@
-python plot_data.py noshow
+# python plot_data.py noshow
+# cd ../data_firing_response/
+# python produce_reduced_data.py noshow
+# cd ../input_impedance_calibration/
+# python minimization.py compute
+# python minimization.py single_comp
+# python minimization.py noshow
+# python produce_all_cell_params.py
+
+/usr/bin/python plot_data.py noshow
 cd ../data_firing_response/
-python produce_reduced_data.py noshow
+/usr/bin/python produce_reduced_data.py noshow
 cd ../input_impedance_calibration/
-python minimization.py compute
-python minimization.py single_comp
-python minimization.py noshow
-python produce_all_cell_params.py
+/usr/bin/python minimization.py compute
+/usr/bin/python minimization.py single_comp
+/usr/bin/python minimization.py noshow
+/usr/bin/python produce_all_cell_params.py

### 2016-09-27 ball_and_rall_tree/final_check_accuracy.py
up fig

@@ -147,7 +147,7 @@ fig, AX = plt.subplots(3, 5, figsize=(10,8))
 plt.subplots_adjust(left=.25, bottom=.25, wspace=.4, hspace=.4)
 # plotting all points in all plots so that they have the same boundaries !!
 YTICKS = [[-70,-60,-50], [3,5,7], [12, 20, 28], [0,15,30]]
-YLIM = [[-75,-30], [1.9,10.], [9,45], [-2,40]]
+YLIM = [[-75,-40], [1.9,8.], [9,31]]
 SV_MINIM = np.load('data/data_minim.npy')
 for EXP, EXP_TH, sv_min, ii in zip(SET_OF_EXPS, SET_OF_EXPS_TH, SV_MINIM, list(range(len(SET_OF_EXPS)))):
     X = EXP['xticks']
@@ -163,8 +163,9 @@ for EXP, EXP_TH, sv_min, ii in zip(SET_OF_EXPS, SET_OF_EXPS_TH, SV_MINIM, list(r
             ax.plot(XTH, sv_min, '--', color='gray', lw=3)
         ax.plot(np.ones(2)*X[1], ylim, 'wD', lw=0, alpha=0., ms=0.01)
         ax.plot(XTH, y2, '-', color='gray', lw=3)
+        ax.plot(X, np.array(y1).mean(axis=1), 'ko-', color='k', alpha=.2)
         ax.errorbar(X, np.array(y1).mean(axis=1),\
-                    yerr=np.array(y1).std(axis=1), color='k', fmt='o', mfc='white')
+                    yerr=np.array(y1).std(axis=1), color='k', fmt='o', mfc='none')
         if (ax in AX[:,-1]):
             ax.set_xscale("log")
             XLIM = [0.005,0.5]
@@ -275,7 +276,7 @@ if __name__=='__main__':
 
             print(synch,np.array([(sexp-sth)**2 for sexp, sth in zip(SV_EXP, SV_TH)]).sum())
             return np.array([(sexp-sth)**2 for sexp, sth in zip(SV_EXP, SV_TH)]).sum()
-        res = minimize(to_minimize, 0.2, options={'maxiter': 5})
+        res = minimize(to_minimize, [0.18], method='TNC', bounds=[(0.15,0.25)])
         print(res)
         SET_OF_EXPS_TH = create_set_of_exps_th(args)
         SV_TH = []

### 2016-09-27 review/response_to_reviewer.txt
up

@@
 
-   The 4 cells represent 4 different cells out of the n=30 cells
+   The 4 cells represent 4 different cells out of the n=27 cells
    recorded in our previous study [[cite:Zerlaut2016]]. The criteria to
@@
 
-  We have updated figure 2C with the mention of "n=30cells" for the
+  We have updated figure 2C with the mention of "n=27cells" for the
   "firing rate dataset", then it highlights the difference with the
@@
 
-  *TO BE DONE*
+  We have verified this statement and we now present the results on
+  Figure 3. The shift in synchrony that minimized the difference
+  between analytical simulations and numerical simulations was found
+  to be +0.18, i.e. close to the 0.2 previously mentionned in the main
+  text (minimum found thanks to a Newton method). Those additional
+  curves are now presented in the middle plots of Figure 3B with the
+  label "estimate, s+=0.18". We also increased the resolution of the
+  scanned points so that we can also have a point close to the s=0.18
+  in the right most column of Figure 3B.  The text now reads (line
+  182): \bf (see Figure 3B, an increase of 0.18 in the synchrony
+  corrects for the ~1mV shift in \(\sigma_V\)) \rm and the legend: \bf
+  In the \(\sigma_V\) plots (middle panels, dashed gray lines), we
+  added the prediction of the analytical estimate after a +0.18
+  correction (found with a Newton method). \rm
 
-Section: "Biophysical origin ..."
+\it Section: "Biophysical origin ..." \rm
 
@@
   logarithmically and not linearly" but we are not sure that this
-  formulation would render better the idea.
+  formulation is a "standard formulation".
 
@@
 
-  Indeed, thanks. We updated the Methods section (mostly the "Model
-  equations" section).
+  Indeed, thanks. We updated the Methods section. Also the densities
+  of synapses were not properly introduced.
 
@@
   Done, it now reads: \bf it extends the approach proposed in Kuhn et
-  al. to the extended dendritic structure following Rall’s branching
-  rule \rm
+  al. to dendritic structures following Rall’s branching rule \rm
 

### 2016-09-28 input_impedance_calibration/investigate_minimization.py
adding all done files

@@ -1,0 +1,226 @@
+import numpy as np
+import matplotlib.pylab as plt
+import os, sys
+sys.path.append('/Users/yzerlaut/work/common_libraries/')
+from graphs.my_graph import set_plot, get_linear_colormap, build_bar_legend, put_list_of_figs_to_svg_fig
+import data_analysis.fourier_for_real as rfft
+sys.path.append('../')
+from theory.analytical_calculus import * # where the core calculus lies
+
+all_freq, all_psd, all_phase = np.load('full_data.npy')
+
+# compute mean
+
+f_bins = np.logspace(np.log(.1)/np.log(10), np.log(all_freq.max())/np.log(10), 20)
+digitized = np.digitize(all_freq, f_bins)
+psd_means = np.array([all_psd[digitized == i].mean() for i in range(1, len(f_bins))])
+psd_std = np.array([all_psd[digitized == i].std() for i in range(1, len(f_bins))])
+phase_means = np.array([all_phase[digitized == i].mean() for i in range(1, len(f_bins))])
+phase_std = np.array([all_phase[digitized == i].std() for i in range(1, len(f_bins))])
+
+f = .5*(f_bins[1:]+f_bins[:-1]) # frequency for theory !!
+#### ================================================== ##
+#### MEAN MODEL PROPERTIES ###############################
+#### ================================================== ##
+
+N = 5
+B = np.arange(N)+2 # to be adjusted !!! (does not depends on N)
+L_soma = np.linspace(5., 20., N)*1e-6
+L_dend = np.linspace(300., 800., N)*1e-6
+D_dend = np.linspace(.5, 4., N)*1e-6
+G_PAS = np.linspace(1e-5, 1e-4, N)*1e4
+CM = np.linspace(.8, 1.8, N)*1e-2
+RA = np.linspace(10., 90., N)*1e-2
+
+soma, stick, params = np.load('../input_impedance_calibration/mean_model.npy')
+try:
+    kept_cells = np.load('../coupling_model/kept_cells.npy')
+except IOError:
+    kept_cells = [True for i in range(30)]
+
+
+def get_input_imped(soma, stick, params):
+    # branching properties
+    params_for_cable_theory(stick, params) # setting cable membrane constants
[…]

### 2016-09-28 input_impedance_calibration/minimization.py

@@ -41,7 +41,6 @@ RA = np.linspace(10., 90., N)*1e-2
 #### MODEL PROPERTIES ###############################
 #### ================================================== ##
 
-
 def get_input_imped(soma, stick, params):
     # branching properties
     params_for_cable_theory(stick, params) # setting cable membrane constants

### 2016-09-28 input_impedance_calibration/show_2_different_neurons.py

@@ -1,0 +1,27 @@
+import numpy as np
+import matplotlib.pylab as plt
+import os, sys
+sys.path.append('../code')
+import my_graph as graph
+sys.path.append('../')
+from theory.analytical_calculus import * # where the core calculus lies
+from .get_calib import *
+from data_firing_response.analyze_data import get_Rm_range
+
+Rm_exp = get_Rm_range()[kept_cells]
+
+imin = np.argmin(Rm_exp)
+imax = np.argmax(Rm_exp)
+print(imin, imax)
+FIGS = []
+AX = []
+
+from theory.brt_drawing import make_fig # where the core calculus lies
+for i in [imin, imax]:
+    soma1, stick1, params1 = adjust_model_prop(Rm_exp[i], soma, stick,\
+                                               precision=.01, maxiter=1e5)
+    fig, ax = make_fig(np.linspace(0, 1, stick1['B']+1)*stick1['L'],
+                        stick1['D'], xscale=1e-6, yscale=50e-6)
+    FIGS.append(fig)
+            
+graph.put_list_of_figs_to_svg_fig(FIGS, visualize=False)

### 2016-09-28 review/response_to_reviewer.txt
update

@@
 5) \it Data extraction. It is not clear how the 4 cells have been selected
-   out of the 27 cells. The 4 cells represent 4 cell types. How are
+   out of the 30 cells. The 4 cells represent 4 cell types. How are
    these cell types specified? The paper does not give an answer on
@@
 
-   The 4 cells represent 4 different cells out of the n=27 cells
+   The 4 cells represent 4 different cells out of the n=30 cells
    recorded in our previous study [[cite:Zerlaut2016]]. The criteria to
@@
 
-  *TO BE DONE*
+#+NAME: fig:var-morpho
+#+CAPTION: *Varying morphology.*
+[[./figs/var_morph.png]]
 
@@
 
-  We have updated figure 2C with the mention of "n=27cells" for the
+  We have updated figure 2C with the mention of "n=30cells" for the
   "firing rate dataset", then it highlights the difference with the
@@
 
-  *TO BE DONE*
+#+NAME: fig:fitting
+#+CAPTION: *Fitting.*
+[[./figs/fitting.png]]
 

### 2016-09-29 review/response_to_reviewer.txt
DONE

@@
 
-   We agree with the reviewer that the formulation "only [...] except
-   [...]" might be misleading, we adapted the abstract to remove this
-   source of confusion. Now it reads: \bf "but trivially, the _main_
-   significant contribution to the various firing response was the
-   different levels of cellular excitability [...]". \rm
+   We agree and have reworded the abstract and discussion to better
+   highlight our main finding and better explicit what we mean by
+   "diverse coupling". We also removed the formulation "only [...]
+   except [...]" that might be misleading. We hope it is now more
+   clear.
 
@@
 
+  We performed this systematic analysis, the results are shown in
+  Figure [[fig:var-morpho]]. We adapted the supplemetary figure S2 in the
+  manuscript, to include those results.
+
 #+NAME: fig:var-morpho
-#+CAPTION: *Varying morphology.*
+#+CAPTION: *Dependency of the fluctuations properties as a function of the morphology parameters* (all parameters are varied of -70% and +70% around those of the mean model, one parameter is varied while all others are fixed to those of the mean model, see Table 1).
+We fixed the presynaptic stimulation to a level of \(\nu_e^p=\nu_e^d\)=0.2Hz, \(\nu_i^p=\nu_i^d\)=1.2Hz and s=0.05.
+(the baseline level).
+Globally, the mean polarization  is poorly affected by the morphology, given the balanced nature of the input and the homogenous spread of synapses on the membrane.
+On the other hand, the morphology parameters strongly affect the properties of the amplitude and speed of the fluctuations.
+(i) Dependency on the branching number.
+Because the branching number has an impact on the area, the number of synapses increases with the number of branches, then the amplitude of the fluctuations strongly decreases with the number of branches because of the law of large numbers.
+(ii) Dependency on the tree length.
+The same argument as in (i) holds.
+The length of the tree increases the number of synapses so that it reduces the amplitude of synapses.
+(iii) Dependency on the tree diameter.
+The same argument as in (i) holds again.
+The diameter of the tree increases the number of synapses so that it reduces the amplitude of synapses.
+(iv) Dependency on the size of the soma.
+Here, this increases only the number of inhibitory synapses at the soma.
+Within this range this has very weak effects on the fluctuations.
+(v) Dependency on the leak conductance.
+The leak conductance sets the amplitude and low pass filtering of individual post-synaptic events (because \(\tau_m \sim C_m / G_L\), though see correction introduced by the ongoing activity in the main text).
+An increasing leak conductance will “shunt” post-synaptic events.
+This lowers the amplitude of the fluctuations and lowers the autocorrelation time of the fluctuations.
+(vi) Dependency on the specific capacitance.
+Again because \(\tau_m \sim C_m / G_L\), an increasing capacitance renders the fluctuations much slower (increasing \(\tau_V\) ).
+Also because PSP events are much slower they lead to reduced amplitude of the fluctuations .
+(vii) Dependency on the intracellular resistivity.
+This has a moderate effect within this range.*
 [[./figs/var_morph.png]]
@@
 
-  *TO BE DONE*
+  We now comment on the flip in vertical order (line 138): \bf In
+  particular, it strongly underestimates the variations of phase
+  shifts at medium and high frequencies (f>20Hz) and the relationship
+  between size and modulus at high frequencies (f>100Hz) is poorly
+  captured. Those discrepancies are likely to be due to the details of
+  dendritic arborescence that are not captured by the strong
+  constraints of our dendritic model (symmetric branching, diameter
+  rules, number of branches, etc...). \rm
 
@@
   Indeed, thanks. We updated the Methods section. Also the densities
-  of synapses were not properly introduced.
+  of synapses and some cable theory parameters have been properly
+  introduced.
 
@@
 
+  To get different couplings, the new tree would need to break the
+  relationship between presynaptic quantities and fluctuations
+  properties (the relationship from fluctuations to spikes is
+  independent). We thus studied the properties of the fluctuations for
+  the trees that had similar goodness to fit with respect to the "mean
+  model" of the main text. We present those results in Figure
+  [[fig:fitting]]. Despite some differences, the fluctuations had similar
+  trends than those discussed within the main text, in particular they
+  all showed the crucial ingredient of this study: the very strong
+  increase in fluctuations speed as a function of proximal activity.
+
+#+ATTR_LATEX: :width .8\linewidth
 #+NAME: fig:fitting
-#+CAPTION: *Fitting.*
+#+CAPTION: *Fluctuations properties for the morphologies with similar goodness to fit.* *(A)* Fluctuation propertis for two randomly choosen cells within the high goodness to fit (<1e-3).
+*(B)* Profile of the goodness to fit over the grid of scanned morphology parameters.
+Shown with two randomly picked examples in different range of goodness to fit.
 [[./figs/fitting.png]]

### 2016-09-29 input_impedance_calibration/investigate_minimization.py

@@ -144,17 +144,20 @@ def find_minimum_with_distance():
         DISTANCE.append(dist)
     return np.array(DISTANCE), np.array(ERROR)
 
-def plot_traces_of_intervals(I1=[1e-9,0.002], I2=[0.01,0.1], I3=[0.1,1.], I4=[1,10.], number=2):
-    VALUE_PSD, VALUE_PHASE = np.load('data_minim.npy')
-    ERROR = VALUE_PSD/VALUE_PSD.mean()*VALUE_PHASE/VALUE_PHASE.mean()
+def plot_traces_of_intervals(I1=[1e-9,0.0003], I2=[0.01,0.2], I3=[0.2,1.], I4=[1.,100.], number=2):
+    DISTANCE, ERROR = find_minimum_with_distance()
 
     FIGS = []
-    for I in [I1, I2, I3, I4]:
+    VAR = np.zeros(4)
+    for I,ii in zip([I1, I2, I3, I4], range(4)):
         sample = np.argwhere((ERROR>I[0]) & (ERROR<I[1]))
+        if I==I4:
+            print(sample)
+        VAR[ii] = np.std(DISTANCE[sample])
         for ii in np.random.randint(len(sample), size=number):
             fig = make_experimental_fig(sample[ii])
             FIGS.append(fig)
-    return FIGS
+    return FIGS, VAR
 
 def make_first_fig():
     DISTANCE, ERROR = find_minimum_with_distance()
@@ -218,9 +221,8 @@ if __name__=='__main__':
         fig = make_second_fig()
         fig.savefig('fig.svg')
     else:
-        FIGS = plot_traces_of_intervals()
-        ii=0
-        for fig in FIGS:
-            fig.savefig('fig'+str(ii)+'.svg')
-            ii+=1
-    # plt.show()
+        FIGS, VAR = plot_traces_of_intervals()
+        # ii=0
+        # for fig in FIGS:
+        #     fig.savefig('fig'+str(ii)+'.svg')
+        #     ii+=1
